---
title: "Keneba Big Study - Seropositivity Cutoffs - Two Populations"
output:
  pdf_document: default
  html_notebook: default
  word_document: default
---
  
First set working directory in the console:  
setwd("/Users/Katie/Desktop/R files from work/Keneba main results/Keneba Analysis/KenebaSPcutoffs")
  
For all antigens, establish seropositive, negative, and possibly indeterminate populations.  
  
Select which category the antigen belongs to based on histogram and understanding of the antigen/pathogen.  
1.	Single population – seronegative   
2.	Single population – seropositive  
**3.	Two populations**  

For dual populations, use FMM or k-means clustering to determine populations, then use probability classification function to place samples into negative, positive, or indeterminate groups.  

```{r setup}
library(mixtools)
library(gcookbook)
library(gplots)
library(ggplot2)
library(dplyr)
library(reshape2)

load("KenebaAnalysis_IgG_v1.RData")
targetupdate <- read.csv("KenebaAntigenKeyv7.csv")

#define probability classification functions
f<-function(x,prob,lambda,mu,sigma,k,k1){
  lista<-order(mu)
  
  lambda<-lambda[lista]
  mu<-mu[lista]	
  sigma<-sigma[lista]	
  
  p<-vector('numeric',k)
  
  for(i in 1:k)p[i]<-lambda[i]*dnorm(x,mu[i],sigma[i])
  
  prob-sum(p[1:k1])/sum(p)
}

f2<-function(x,prob,lambda,mu,sigma,k,k1){
  lista<-order(mu)
  
  lambda<-lambda[lista]
  mu<-mu[lista]	
  sigma<-sigma[lista]	
  
  p<-vector('numeric',k)
  
  for(i in 1:k)p[i]<-lambda[i]*dnorm(x,mu[i],sigma[i])
  
  prob-sum(p[k1:k])/sum(p)
}

```

1. Identify antigens with two populations.   
IgG first - listed as "two" in antigen key v7.  
```{r}
burritos2 <- burritos[,(ncol(target_meta2.df)+1):ncol(burritos)]
rownames(burritos2) <- burritos$Name

burritos3 <- merge(targetupdate, burritos2, by.y = "row.names", by.x = "Name")

multants <- filter(burritos3, SP_group_IgG == "two")
rownames(multants) <- make.names(multants$Name)
multantnames <- rownames(multants)
```

2. Set up stuff which will be used for all antigens. Save a cutoff below which is negative,  a cutoff above which is positive, for both kmeans and fmm. Indeterminate samples will be in the middle of those two cutoffs. use greater than or equal and less than or equal.  
Note: The probability classification function may fail for one or both models.  This may mean that there is no point in the data for which there is a greater than 90% (that's the cutoff I'm choosing, based on Nuno and Gillian's paper) probability that the data is in the positive of the two populations. 
```{r}
multcutoffs <- as.data.frame(matrix(ncol = 6, nrow = length(multantnames))) 
colnames(multcutoffs) <- c("Name", "kmeans.neg", "kmeans.pos", "fmm.neg", "fmm.pos", "BestModel")
multcutoffs$Name <- multantnames

multprevalence <- as.data.frame(matrix(ncol = 7, nrow = length(multantnames))) 
colnames(multprevalence) <- c("Name", "kmeans.neg", "kmeans.pos", "kmeans.indet", "fmm.neg", "fmm.pos", "fmm.indet")
multprevalence$Name <- multantnames
```

3. Go through the two or three population antigens one by one and identify what looks reasonable based on histograms previously generated, then do K-means and FMM. 
  
4.FMM:    
-- Run fmm and probability classification function (and plot this) and store cutoffs. On this plot, the blue line is component 1 and the purple line is component 2 of the fmm. 
-- **FMM Strategy: Run the FMM ten times to check consistency. If inconsistent, go with model with higher Loglik or the one that looks more like positive and negative rather than the two country populations and put in the parameters for both mu and sigma from that model, this will hopefully cause the solution to be the same every time in the future. Also, if the multiple solutions for the FMM do not match what looks right based on the histograms of the overall data and country density plots, put in estimates for BOTH mu and sigma and see if this helps find another solution. **
-- Plot histograms showing all data, cutoffs (positive and negative) and normal distribution curves added.
    
5. K-means:    
-- Run k-means clustering and use mean and sd of the two or three populations for  
probability classification function. plot this and store cutoffs.  
-- Plot histograms showing all data, cutoffs (positive and negative) and normal distribution curves added.

Note: 
If both FMM and K means are not working for a lot of antigens... what about eyeballing the cutoff between the two populations (visual k-means clustering haha) but then still using the probability classification function to determine seropositivity!! I think this could work because the main problem I run into is that the algorithms are not distinguishing between the populations well. 

Or: go back to making sure the negative population is well identified or the positive population well identified and then doing the mean plus sd thing again.

Or: For the antigens for which the seroreactivity in the UK population should be and looks negative, could consider using the UK negative population rather than FMM. 

1 - X800E2A - good candidate for negative FMM population + 3SD, or UK population + 3SD, negative probability never above 0.9
```{r}
i = 1
#Select antigen
antigen <- multantnames[i]
antigen

#subset data for this antigen
singleant <- c(as.matrix(multants[i, (ncol(targetupdate)+1):ncol(multants)]))
#singleant <- singleant[singleant >= 0]

#put the data in numerical order - required to generate probability classification plot below
antibody1 <- sort(singleant)

#### Try FMM model first

fit.ab2<-normalmixEM(antibody1, lambda = c(0.5, 0.5), k = 2, mu = c(-1.517397, 0.196742), sigma = c(0.516787, 1.365747), fast=FALSE,maxit=10000,epsilon = 1e-16,maxrestarts=1000)

#5 Plot Cut off Value
summary(fit.ab2)

#cutoff below which is negative - manually set interval end points
#cutoff<-uniroot(f,c(-4,-1),prob=0.90,lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=1)$root

#cutoff above which is positive - manually set interval end points
cutoff2<-uniroot(f2,c(-1,0),prob=0.90, lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=2)$root

#multcutoffs[i,4] <- cutoff
multcutoffs[i,5] <- cutoff2

#percentage positive 
pos <- sum(antibody1>cutoff2)/length(antibody1) * 100

#percentage negative
#neg <- sum(antibody1<cutoff)/length(antibody1) * 100

#percentage indeterminate
#indet <- (1-sum(antibody1>cutoff2)/length(antibody1)-sum(antibody1<cutoff)/length(antibody1)) *100

#multprevalence[i,5] <- neg
multprevalence[i,6] <- pos
#multprevalence[i,7] <- indet

#Plot cutoffs if there are two
{plot(antibody1,fit.ab2$posterior[,1],type='n',xlim=c(-4,10),lwd=2,ylim=c(0,1),col='green',las=1,xlab='Log2(MFI Ratio)',ylab='classification probability', main = paste(antigen, "FMM"))

#rect(cutoff,-0.04,cutoff2,1.04,col='light grey',lwd=1.5)
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='red')

abline(h=0.90,lwd=1.5,lty=2)
#abline(v=cutoff,lwd=1)
abline(v=cutoff2,lwd=1)

lines(antibody1,fit.ab2$posterior[,1],lwd=2,col='blue')
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='purple')
legend(1125,0.8,c(expression(S^'-'),expression(S^'+')),lty=c(1,1),lwd=2,col=c('blue','purple'))}

#Plot histogram with cutoffs shown and normal distributions shown
{hist(antibody1, prob = TRUE, breaks=50, main = paste(antigen, "FMM"), 
  xlab="Normalized Log2(MFI Ratio)", cex.main=0.9, cex.lab=0.8, 
  cex.axis = 0.8, xlim=c(-4,9), ylim = c(0,0.7))
curve(dnorm(x, fit.ab2$mu[1], fit.ab2$sigma[1]), add=TRUE, col="darkblue", lwd=2)
curve(dnorm(x, fit.ab2$mu[2], fit.ab2$sigma[2]), add=TRUE, col="darkblue", lwd=2)
abline(v = multcutoffs[i,5], col = "red", lty = 2, lwd = 0.7, xpd=FALSE)
}

remove(antigen, antibody1, cutoff, cutoff2, neg, pos, indet, fit.ab2)
```



2 - X800E2C
```{r}
i = 2
#Select antigen
antigen <- multantnames[i]
antigen

#subset data for this antigen
singleant <- c(as.matrix(multants[i, (ncol(targetupdate)+1):ncol(multants)]))
#singleant <- singleant[singleant >= 0]

#put the data in numerical order - required to generate probability classification plot below
antibody1 <- sort(singleant)

#### Try FMM model first

fit.ab2<-normalmixEM(antibody1, lambda = c(0.5, 0.5), mu = c(-1.3,.8), sigma = c(0.813028, 0.797697), k = 2, fast=FALSE,maxit=10000,epsilon = 1e-16,maxrestarts=1000)

#5 Plot Cut off Value
summary(fit.ab2)

#cutoff below which is negative - manually set interval end points
cutoff<-uniroot(f,c(-2,1),prob=0.90,lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=1)$root

#cutoff above which is positive - manually set interval end points
cutoff2<-uniroot(f2,c(-1,3),prob=0.90, lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=2)$root

multcutoffs[i,4] <- cutoff
multcutoffs[i,5] <- cutoff2

#percentage positive 
pos <- sum(antibody1>cutoff2)/length(antibody1) * 100

#percentage negative
neg <- sum(antibody1<cutoff)/length(antibody1) * 100

#percentage indeterminate
indet <- (1-sum(antibody1>cutoff2)/length(antibody1)-sum(antibody1<cutoff)/length(antibody1)) *100

multprevalence[i,5] <- neg
multprevalence[i,6] <- pos
multprevalence[i,7] <- indet

#Plot cutoffs if there are two
{plot(antibody1,fit.ab2$posterior[,1],type='n',xlim=c(-4,10),lwd=2,ylim=c(0,1),col='green',las=1,xlab='Log2(MFI Ratio)',ylab='classification probability', main = paste(antigen, "FMM"))

rect(cutoff,-0.04,cutoff2,1.04,col='light grey',lwd=1.5)
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='red')

abline(h=0.90,lwd=1.5,lty=2)
abline(v=cutoff,lwd=1)
abline(v=cutoff2,lwd=1)

lines(antibody1,fit.ab2$posterior[,1],lwd=2,col='blue')
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='purple')
legend(1125,0.8,c(expression(S^'-'),expression(S^'+')),lty=c(1,1),lwd=2,col=c('blue','purple'))}

#Plot histogram with cutoffs shown and normal distributions shown
{hist(antibody1, prob = TRUE, breaks=50, main = paste(antigen, "FMM"), 
  xlab="Normalized Log2(MFI Ratio)", cex.main=0.9, cex.lab=0.8, 
  cex.axis = 0.8, xlim=c(-4,9), ylim = c(0,0.7))
curve(dnorm(x, fit.ab2$mu[1], fit.ab2$sigma[1]), add=TRUE, col="darkblue", lwd=2)
curve(dnorm(x, fit.ab2$mu[2], fit.ab2$sigma[2]), add=TRUE, col="darkblue", lwd=2)
abline(v = multcutoffs[i,4:5], col = "red", lty = 2, lwd = 0.7, xpd=FALSE)}

remove(antigen, antibody1, cutoff, cutoff2, neg, pos, indet, fit.ab2)
```

3 - X800E2D
```{r}
i = 3
#Select antigen
antigen <- multantnames[i]
antigen

#subset data for this antigen
singleant <- c(as.matrix(multants[i, (ncol(targetupdate)+1):ncol(multants)]))
#singleant <- singleant[singleant >= 0]

#put the data in numerical order - required to generate probability classification plot below
antibody1 <- sort(singleant)

#### Try FMM model first

fit.ab2<-normalmixEM(antibody1, lambda = c(0.5, 0.5), k = 2, mu = c(-0.564083, 1.435319), sigma = c(1.044024, 0.969998),fast=FALSE,maxit=10000,epsilon = 1e-16,maxrestarts=1000)

#5 Plot Cut off Value
summary(fit.ab2)

#cutoff below which is negative - manually set interval end points
cutoff<-uniroot(f,c(-4,0),prob=0.90,lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=1)$root

#cutoff above which is positive - manually set interval end points
cutoff2<-uniroot(f2,c(0,6),prob=0.90, lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=2)$root

multcutoffs[i,4] <- cutoff
multcutoffs[i,5] <- cutoff2

#percentage positive 
pos <- sum(antibody1>cutoff2)/length(antibody1) * 100

#percentage negative
neg <- sum(antibody1<cutoff)/length(antibody1) * 100

#percentage indeterminate
indet <- (1-sum(antibody1>cutoff2)/length(antibody1)-sum(antibody1<cutoff)/length(antibody1)) *100

multprevalence[i,5] <- neg
multprevalence[i,6] <- pos
multprevalence[i,7] <- indet

#Plot cutoffs if there are two
{plot(antibody1,fit.ab2$posterior[,1],type='n',xlim=c(-4,10),lwd=2,ylim=c(0,1),col='green',las=1,xlab='Log2(MFI Ratio)',ylab='classification probability', main = paste(antigen, "FMM"))

rect(cutoff,-0.04,cutoff2,1.04,col='light grey',lwd=1.5)
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='red')

abline(h=0.90,lwd=1.5,lty=2)
abline(v=cutoff,lwd=1)
abline(v=cutoff2,lwd=1)

lines(antibody1,fit.ab2$posterior[,1],lwd=2,col='blue')
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='purple')
legend(1125,0.8,c(expression(S^'-'),expression(S^'+')),lty=c(1,1),lwd=2,col=c('blue','purple'))}

#Plot histogram with cutoffs shown and normal distributions shown
{hist(antibody1, prob = TRUE, breaks=50, main = paste(antigen, "FMM"), 
  xlab="Normalized Log2(MFI Ratio)", cex.main=0.9, cex.lab=0.8, 
  cex.axis = 0.8, xlim=c(-4,9), ylim = c(0,0.6))
curve(dnorm(x, fit.ab2$mu[1], fit.ab2$sigma[1]), add=TRUE, col="darkblue", lwd=2)
curve(dnorm(x, fit.ab2$mu[2], fit.ab2$sigma[2]), add=TRUE, col="darkblue", lwd=2)
abline(v = multcutoffs[i,4:5], col = "red", lty = 2, lwd = 0.7, xpd=FALSE)}

remove(antigen, antibody1, cutoff, cutoff2, neg, pos, indet, fit.ab2)
```



4 - X800PRISM - the negative never reaches probability above 0.9
```{r}
i = 4
#Select antigen
antigen <- multantnames[i]
antigen

#subset data for this antigen
singleant <- c(as.matrix(multants[i, (ncol(targetupdate)+1):ncol(multants)]))
#singleant <- singleant[singleant >= 0]

#put the data in numerical order - required to generate probability classification plot below
antibody1 <- sort(singleant)

#### Try FMM model first

fit.ab2<-normalmixEM(antibody1, lambda = c(0.5, 0.5),mu = c(-1.520649,0.611313), sigma = c(0.747110, 0.986087), k = 2, fast=FALSE,maxit=10000,epsilon = 1e-16,maxrestarts=1000)

#5 Plot Cut off Value
summary(fit.ab2)

#cutoff below which is negative - manually set interval end points
cutoff<-uniroot(f,c(-4,0),prob=0.90,lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=1)$root

#cutoff above which is positive - manually set interval end points
cutoff2<-uniroot(f2,c(-1,6),prob=0.90, lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=2)$root

multcutoffs[i,4] <- cutoff
multcutoffs[i,5] <- cutoff2

#percentage positive 
pos <- sum(antibody1>cutoff2)/length(antibody1) * 100

#percentage negative
neg <- sum(antibody1<cutoff)/length(antibody1) * 100

#percentage indeterminate
indet <- (1-sum(antibody1>cutoff2)/length(antibody1)-sum(antibody1<cutoff)/length(antibody1)) *100

multprevalence[i,5] <- neg
multprevalence[i,6] <- pos
multprevalence[i,7] <- indet

#Plot cutoffs if there are two
{plot(antibody1,fit.ab2$posterior[,1],type='n',xlim=c(-4,10),lwd=2,ylim=c(0,1),col='green',las=1,xlab='Log2(MFI Ratio)',ylab='classification probability', main = paste(antigen, "FMM"))

rect(cutoff,-0.04,cutoff2,1.04,col='light grey',lwd=1.5)
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='red')

abline(h=0.90,lwd=1.5,lty=2)
abline(v=cutoff,lwd=1)
abline(v=cutoff2,lwd=1)

lines(antibody1,fit.ab2$posterior[,1],lwd=2,col='blue')
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='purple')
legend(1125,0.8,c(expression(S^'-'),expression(S^'+')),lty=c(1,1),lwd=2,col=c('blue','purple'))}

#Plot histogram with cutoffs shown and normal distributions shown
{hist(antibody1, prob = TRUE, breaks=50, main = paste(antigen, "FMM"), 
  xlab="Normalized Log2(MFI Ratio)", cex.main=0.9, cex.lab=0.8, 
  cex.axis = 0.8, xlim=c(-4,9), ylim = c(0,0.6))
curve(dnorm(x, fit.ab2$mu[1], fit.ab2$sigma[1]), add=TRUE, col="darkblue", lwd=2)
curve(dnorm(x, fit.ab2$mu[2], fit.ab2$sigma[2]), add=TRUE, col="darkblue", lwd=2)
abline(v = multcutoffs[i,4:5], col = "red", lty = 2, lwd = 0.7, xpd=FALSE)}

remove(antigen, antibody1, cutoff, cutoff2, neg, pos, indet, fit.ab2)
```


5 - Ascaris
```{r}
i = 5
#Select antigen
antigen <- multantnames[i]
antigen

#subset data for this antigen
singleant <- c(as.matrix(multants[i, (ncol(targetupdate)+1):ncol(multants)]))
#singleant <- singleant[singleant >= 0]

#put the data in numerical order - required to generate probability classification plot below
antibody1 <- sort(singleant)

#### Try FMM model first

fit.ab2<-normalmixEM(antibody1, lambda = c(0.5, 0.5), k = 2,mu = c(4.406267,2.598272), sigma = c(0.797413, 1.034637), fast=FALSE,maxit=10000,epsilon = 1e-16,maxrestarts=1000)

#5 Plot Cut off Value
summary(fit.ab2)

#cutoff below which is negative - manually set interval end points
cutoff<-uniroot(f,c(-1,4),prob=0.90,lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=1)$root

#cutoff above which is positive - manually set interval end points
cutoff2<-uniroot(f2,c(3,8),prob=0.90, lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=2)$root

multcutoffs[i,4] <- cutoff
multcutoffs[i,5] <- cutoff2

#percentage positive 
pos <- sum(antibody1>cutoff2)/length(antibody1) * 100

#percentage negative
neg <- sum(antibody1<cutoff)/length(antibody1) * 100

#percentage indeterminate
indet <- (1-sum(antibody1>cutoff2)/length(antibody1)-sum(antibody1<cutoff)/length(antibody1)) *100

multprevalence[i,5] <- neg
multprevalence[i,6] <- pos
multprevalence[i,7] <- indet

#Plot cutoffs if there are two
{plot(antibody1,fit.ab2$posterior[,1],type='n',xlim=c(-4,10),lwd=2,ylim=c(0,1),col='green',las=1,xlab='Log2(MFI Ratio)',ylab='classification probability', main = paste(antigen, "FMM"))

rect(cutoff,-0.04,cutoff2,1.04,col='light grey',lwd=1.5)
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='red')

abline(h=0.90,lwd=1.5,lty=2)
abline(v=cutoff,lwd=1)
abline(v=cutoff2,lwd=1)

lines(antibody1,fit.ab2$posterior[,1],lwd=2,col='blue')
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='purple')
legend(1125,0.8,c(expression(S^'-'),expression(S^'+')),lty=c(1,1),lwd=2,col=c('blue','purple'))}

#Plot histogram with cutoffs shown and normal distributions shown
{hist(antibody1, prob = TRUE, breaks=50, main = paste(antigen, "FMM"), 
  xlab="Normalized Log2(MFI Ratio)", cex.main=0.9, cex.lab=0.8, 
  cex.axis = 0.8, xlim=c(-4,9), ylim = c(0,0.5))
curve(dnorm(x, fit.ab2$mu[1], fit.ab2$sigma[1]), add=TRUE, col="darkblue", lwd=2)
curve(dnorm(x, fit.ab2$mu[2], fit.ab2$sigma[2]), add=TRUE, col="darkblue", lwd=2)
abline(v = multcutoffs[i,4:5], col = "red", lty = 2, lwd = 0.7, xpd=FALSE)}

remove(antigen, antibody1, cutoff, cutoff2, neg, pos, indet, fit.ab2)
```

6 - BP.FHA
```{r}
i = 6
#Select antigen
antigen <- multantnames[i]
antigen

#subset data for this antigen
singleant <- c(as.matrix(multants[i, (ncol(targetupdate)+1):ncol(multants)]))
#singleant <- singleant[singleant >= 0]

#put the data in numerical order - required to generate probability classification plot below
antibody1 <- sort(singleant)

#### Try FMM model first

fit.ab2<-normalmixEM(antibody1, lambda = c(0.5, 0.5), k = 2, mu = c(3.697882, 5.265963), sigma = c(1.518228, 0.847783), fast=FALSE,maxit=10000,epsilon = 1e-16,maxrestarts=1000)

#5 Plot Cut off Value
summary(fit.ab2)

#cutoff below which is negative - manually set interval end points
cutoff<-uniroot(f,c(-2,4),prob=0.90,lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=1)$root

#cutoff above which is positive - manually set interval end points
#cutoff2<-uniroot(f2,c(3,8),prob=0.90, lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=2)$root

multcutoffs[i,4] <- cutoff
#multcutoffs[i,5] <- cutoff2

#percentage positive 
#pos <- sum(antibody1>cutoff2)/length(antibody1) * 100

#percentage negative
neg <- sum(antibody1<cutoff)/length(antibody1) * 100

#percentage indeterminate
#indet <- (1-sum(antibody1>cutoff2)/length(antibody1)-sum(antibody1<cutoff)/length(antibody1)) *100

multprevalence[i,5] <- neg
#multprevalence[i,6] <- pos
#multprevalence[i,7] <- indet

#Plot cutoffs if there are two
{plot(antibody1,fit.ab2$posterior[,1],type='n',xlim=c(-4,10),lwd=2,ylim=c(0,1),col='green',las=1,xlab='Log2(MFI Ratio)',ylab='classification probability', main = paste(antigen, "FMM"))

#rect(cutoff,-0.04,cutoff2,1.04,col='light grey',lwd=1.5)
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='red')

abline(h=0.90,lwd=1.5,lty=2)
abline(v=cutoff,lwd=1)
#abline(v=cutoff2,lwd=1)

lines(antibody1,fit.ab2$posterior[,1],lwd=2,col='blue')
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='purple')
legend(1125,0.8,c(expression(S^'-'),expression(S^'+')),lty=c(1,1),lwd=2,col=c('blue','purple'))}

#Plot histogram with cutoffs shown and normal distributions shown
{hist(antibody1, prob = TRUE, breaks=50, main = paste(antigen, "FMM"), 
  xlab="Normalized Log2(MFI Ratio)", cex.main=0.9, cex.lab=0.8, 
  cex.axis = 0.8, xlim=c(-4,9), ylim = c(0,0.5))
curve(dnorm(x, fit.ab2$mu[1], fit.ab2$sigma[1]), add=TRUE, col="darkblue", lwd=2)
curve(dnorm(x, fit.ab2$mu[2], fit.ab2$sigma[2]), add=TRUE, col="darkblue", lwd=2)
abline(v = multcutoffs[i,4], col = "red", lty = 2, lwd = 0.7, xpd=FALSE)}

remove(antigen, antibody1, cutoff, cutoff2, neg, pos, indet, fit.ab2)
```

7 - BP.T - negative probability never above 0.9
```{r}
i = 7
#Select antigen
antigen <- multantnames[i]
antigen

#subset data for this antigen
singleant <- c(as.matrix(multants[i, (ncol(targetupdate)+1):ncol(multants)]))
#singleant <- singleant[singleant >= 0]

#put the data in numerical order - required to generate probability classification plot below
antibody1 <- sort(singleant)

#### Try FMM model first

fit.ab2<-normalmixEM(antibody1, lambda = c(0.5, 0.5), k = 2, fast=FALSE,maxit=10000,epsilon = 1e-16,maxrestarts=1000)

#5 Plot Cut off Value
summary(fit.ab2)

#cutoff below which is negative - manually set interval end points
#cutoff<-uniroot(f,c(-4,0.5),prob=0.90,lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=1)$root

#cutoff above which is positive - manually set interval end points
cutoff2<-uniroot(f2,c(1,3),prob=0.90, lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=2)$root

#multcutoffs[i,4] <- cutoff
multcutoffs[i,5] <- cutoff2

#percentage positive 
pos <- sum(antibody1>cutoff2)/length(antibody1) * 100

#percentage negative
#neg <- sum(antibody1<cutoff)/length(antibody1) * 100

#percentage indeterminate
#indet <- (1-sum(antibody1>cutoff2)/length(antibody1)-sum(antibody1<cutoff)/length(antibody1)) *100

#multprevalence[i,5] <- neg
multprevalence[i,6] <- pos
#multprevalence[i,7] <- indet

#Plot cutoffs if there are two
{plot(antibody1,fit.ab2$posterior[,1],type='n',xlim=c(-4,10),lwd=2,ylim=c(0,1),col='green',las=1,xlab='Log2(MFI Ratio)',ylab='classification probability', main = paste(antigen, "FMM"))

#rect(cutoff,-0.04,cutoff2,1.04,col='light grey',lwd=1.5)
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='red')

abline(h=0.90,lwd=1.5,lty=2)
#abline(v=cutoff,lwd=1)
abline(v=cutoff2,lwd=1)

lines(antibody1,fit.ab2$posterior[,1],lwd=2,col='blue')
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='purple')
legend(1125,0.8,c(expression(S^'-'),expression(S^'+')),lty=c(1,1),lwd=2,col=c('blue','purple'))}

#Plot histogram with cutoffs shown and normal distributions shown
{hist(antibody1, prob = TRUE, breaks=50, main = paste(antigen, "FMM"), 
  xlab="Normalized Log2(MFI Ratio)", cex.main=0.9, cex.lab=0.8, 
  cex.axis = 0.8, xlim=c(-4,9), ylim = c(0,0.6))
curve(dnorm(x, fit.ab2$mu[1], fit.ab2$sigma[1]), add=TRUE, col="darkblue", lwd=2)
curve(dnorm(x, fit.ab2$mu[2], fit.ab2$sigma[2]), add=TRUE, col="darkblue", lwd=2)
abline(v = multcutoffs[i,5], col = "red", lty = 2, lwd = 0.7, xpd=FALSE)}

remove(antigen, antibody1, cutoff, cutoff2, neg, pos, indet, fit.ab2)
```

8 - BP.Whole.Cell
```{r}
i = 8
#Select antigen
antigen <- multantnames[i]
antigen

#subset data for this antigen
singleant <- c(as.matrix(multants[i, (ncol(targetupdate)+1):ncol(multants)]))
#singleant <- singleant[singleant >= 0]

#put the data in numerical order - required to generate probability classification plot below
antibody1 <- sort(singleant)

#### Try FMM model first

fit.ab2<-normalmixEM(antibody1, lambda = c(0.5, 0.5), k = 2, fast=FALSE,maxit=10000,epsilon = 1e-16,maxrestarts=1000)

#5 Plot Cut off Value
summary(fit.ab2)

#cutoff below which is negative - manually set interval end points
cutoff<-uniroot(f,c(0,2),prob=0.90,lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=1)$root

#cutoff above which is positive - manually set interval end points
cutoff2<-uniroot(f2,c(2,8),prob=0.90, lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=2)$root

multcutoffs[i,4] <- cutoff
multcutoffs[i,5] <- cutoff2

#percentage positive 
pos <- sum(antibody1>cutoff2)/length(antibody1) * 100

#percentage negative
neg <- sum(antibody1<cutoff)/length(antibody1) * 100

#percentage indeterminate
indet <- (1-sum(antibody1>cutoff2)/length(antibody1)-sum(antibody1<cutoff)/length(antibody1)) *100

multprevalence[i,5] <- neg
multprevalence[i,6] <- pos
multprevalence[i,7] <- indet

#Plot cutoffs if there are two
{plot(antibody1,fit.ab2$posterior[,1],type='n',xlim=c(-4,10),lwd=2,ylim=c(0,1),col='green',las=1,xlab='Log2(MFI Ratio)',ylab='classification probability', main = paste(antigen, "FMM"))

rect(cutoff,-0.04,cutoff2,1.04,col='light grey',lwd=1.5)
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='red')

abline(h=0.90,lwd=1.5,lty=2)
abline(v=cutoff,lwd=1)
abline(v=cutoff2,lwd=1)

lines(antibody1,fit.ab2$posterior[,1],lwd=2,col='blue')
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='purple')
legend(1125,0.8,c(expression(S^'-'),expression(S^'+')),lty=c(1,1),lwd=2,col=c('blue','purple'))}

#Plot histogram with cutoffs shown and normal distributions shown
{hist(antibody1, prob = TRUE, breaks=50, main = paste(antigen, "FMM"), 
  xlab="Normalized Log2(MFI Ratio)", cex.main=0.9, cex.lab=0.8, 
  cex.axis = 0.8, xlim=c(-4,9), ylim = c(0,0.7))
curve(dnorm(x, fit.ab2$mu[1], fit.ab2$sigma[1]), add=TRUE, col="darkblue", lwd=2)
curve(dnorm(x, fit.ab2$mu[2], fit.ab2$sigma[2]), add=TRUE, col="darkblue", lwd=2)
abline(v = multcutoffs[i,4:5], col = "red", lty = 2, lwd = 0.7, xpd=FALSE)}

remove(antigen, antibody1, cutoff, cutoff2, neg, pos, indet, fit.ab2)
```


9 - CMV.GradeIII
```{r}
i = 9
#Select antigen
antigen <- multantnames[i]
antigen

#subset data for this antigen
singleant <- c(as.matrix(multants[i, (ncol(targetupdate)+1):ncol(multants)]))
#singleant <- singleant[singleant >= 0]

#put the data in numerical order - required to generate probability classification plot below
antibody1 <- sort(singleant)

#### Try FMM model first

fit.ab2<-normalmixEM(antibody1, lambda = c(0.5, 0.5), k = 2, fast=FALSE,maxit=10000,epsilon = 1e-16,maxrestarts=1000)

#5 Plot Cut off Value
summary(fit.ab2)

#cutoff below which is negative - manually set interval end points
cutoff<-uniroot(f,c(0,2),prob=0.90,lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=1)$root

#cutoff above which is positive - manually set interval end points
cutoff2<-uniroot(f2,c(2,8),prob=0.90, lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=2)$root

multcutoffs[i,4] <- cutoff
multcutoffs[i,5] <- cutoff2

#percentage positive 
pos <- sum(antibody1>cutoff2)/length(antibody1) * 100

#percentage negative
neg <- sum(antibody1<cutoff)/length(antibody1) * 100

#percentage indeterminate
indet <- (1-sum(antibody1>cutoff2)/length(antibody1)-sum(antibody1<cutoff)/length(antibody1)) *100

multprevalence[i,5] <- neg
multprevalence[i,6] <- pos
multprevalence[i,7] <- indet

#Plot cutoffs if there are two
{plot(antibody1,fit.ab2$posterior[,1],type='n',xlim=c(-4,10),lwd=2,ylim=c(0,1),col='green',las=1,xlab='Log2(MFI Ratio)',ylab='classification probability', main = paste(antigen, "FMM"))

rect(cutoff,-0.04,cutoff2,1.04,col='light grey',lwd=1.5)
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='red')

abline(h=0.90,lwd=1.5,lty=2)
abline(v=cutoff,lwd=1)
abline(v=cutoff2,lwd=1)

lines(antibody1,fit.ab2$posterior[,1],lwd=2,col='blue')
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='purple')
legend(1125,0.8,c(expression(S^'-'),expression(S^'+')),lty=c(1,1),lwd=2,col=c('blue','purple'))}

#Plot histogram with cutoffs shown and normal distributions shown
{hist(antibody1, prob = TRUE, breaks=50, main = paste(antigen, "FMM"), 
  xlab="Normalized Log2(MFI Ratio)", cex.main=0.9, cex.lab=0.8, 
  cex.axis = 0.8, xlim=c(-4,9), ylim = c(0,0.7))
curve(dnorm(x, fit.ab2$mu[1], fit.ab2$sigma[1]), add=TRUE, col="darkblue", lwd=2)
curve(dnorm(x, fit.ab2$mu[2], fit.ab2$sigma[2]), add=TRUE, col="darkblue", lwd=2)
abline(v = multcutoffs[i,4:5], col = "red", lty = 2, lwd = 0.7, xpd=FALSE)}

remove(antigen, antibody1, cutoff, cutoff2, neg, pos, indet, fit.ab2)
```


10 - CMV.pp150 
```{r}
i = 10
#Select antigen
antigen <- multantnames[i]
antigen

#subset data for this antigen
singleant <- c(as.matrix(multants[i, (ncol(targetupdate)+1):ncol(multants)]))
#singleant <- singleant[singleant >= 0]

#put the data in numerical order - required to generate probability classification plot below
antibody1 <- sort(singleant)

#### Try FMM model first

fit.ab2<-normalmixEM(antibody1, lambda = c(0.5, 0.5), k = 2, fast=FALSE,maxit=10000,epsilon = 1e-16,maxrestarts=1000)

#5 Plot Cut off Value
summary(fit.ab2)

#cutoff below which is negative - manually set interval end points
cutoff<-uniroot(f,c(0,2),prob=0.90,lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=1)$root

#cutoff above which is positive - manually set interval end points
cutoff2<-uniroot(f2,c(0.5,4),prob=0.90, lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=2)$root

multcutoffs[i,4] <- cutoff
multcutoffs[i,5] <- cutoff2

#percentage positive 
pos <- sum(antibody1>cutoff2)/length(antibody1) * 100

#percentage negative
neg <- sum(antibody1<cutoff)/length(antibody1) * 100

#percentage indeterminate
indet <- (1-sum(antibody1>cutoff2)/length(antibody1)-sum(antibody1<cutoff)/length(antibody1)) *100

multprevalence[i,5] <- neg
multprevalence[i,6] <- pos
multprevalence[i,7] <- indet

#Plot cutoffs if there are two
{plot(antibody1,fit.ab2$posterior[,1],type='n',xlim=c(-4,10),lwd=2,ylim=c(0,1),col='green',las=1,xlab='Log2(MFI Ratio)',ylab='classification probability', main = paste(antigen, "FMM"))

rect(cutoff,-0.04,cutoff2,1.04,col='light grey',lwd=1.5)
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='red')

abline(h=0.90,lwd=1.5,lty=2)
abline(v=cutoff,lwd=1)
abline(v=cutoff2,lwd=1)

lines(antibody1,fit.ab2$posterior[,1],lwd=2,col='blue')
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='purple')
legend(1125,0.8,c(expression(S^'-'),expression(S^'+')),lty=c(1,1),lwd=2,col=c('blue','purple'))}

#Plot histogram with cutoffs shown and normal distributions shown
{hist(antibody1, prob = TRUE, breaks=50, main = paste(antigen, "FMM"), 
  xlab="Normalized Log2(MFI Ratio)", cex.main=0.9, cex.lab=0.8, 
  cex.axis = 0.8, xlim=c(-4,10), ylim = c(0,0.5))
curve(dnorm(x, fit.ab2$mu[1], fit.ab2$sigma[1]), add=TRUE, col="darkblue", lwd=2)
curve(dnorm(x, fit.ab2$mu[2], fit.ab2$sigma[2]), add=TRUE, col="darkblue", lwd=2)
abline(v = multcutoffs[i,4:5], col = "red", lty = 2, lwd = 0.7, xpd=FALSE)}

remove(antigen, antibody1, cutoff, cutoff2, neg, pos, indet, fit.ab2)
```

11 - DT.NIBSC
```{r}
i = 11
#Select antigen
antigen <- multantnames[i]
antigen

#subset data for this antigen
singleant <- c(as.matrix(multants[i, (ncol(targetupdate)+1):ncol(multants)]))
#singleant <- singleant[singleant >= 0]

#put the data in numerical order - required to generate probability classification plot below
antibody1 <- sort(singleant)

#### Try FMM model first

fit.ab2<-normalmixEM(antibody1, lambda = c(0.5, 0.5), k = 2, fast=FALSE,maxit=10000,epsilon = 1e-16,maxrestarts=1000)

#5 Plot Cut off Value
summary(fit.ab2)

#cutoff below which is negative - manually set interval end points
cutoff<-uniroot(f,c(0,3),prob=0.90,lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=1)$root

#cutoff above which is positive - manually set interval end points
cutoff2<-uniroot(f2,c(2,8),prob=0.90, lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=2)$root

multcutoffs[i,4] <- cutoff
multcutoffs[i,5] <- cutoff2

#percentage positive 
pos <- sum(antibody1>cutoff2)/length(antibody1) * 100

#percentage negative
neg <- sum(antibody1<cutoff)/length(antibody1) * 100

#percentage indeterminate
indet <- (1-sum(antibody1>cutoff2)/length(antibody1)-sum(antibody1<cutoff)/length(antibody1)) *100

multprevalence[i,5] <- neg
multprevalence[i,6] <- pos
multprevalence[i,7] <- indet

#Plot cutoffs if there are two
{plot(antibody1,fit.ab2$posterior[,1],type='n',xlim=c(-4,10),lwd=2,ylim=c(0,1),col='green',las=1,xlab='Log2(MFI Ratio)',ylab='classification probability', main = paste(antigen, "FMM"))

rect(cutoff,-0.04,cutoff2,1.04,col='light grey',lwd=1.5)
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='red')

abline(h=0.90,lwd=1.5,lty=2)
abline(v=cutoff,lwd=1)
abline(v=cutoff2,lwd=1)

lines(antibody1,fit.ab2$posterior[,1],lwd=2,col='blue')
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='purple')
legend(1125,0.8,c(expression(S^'-'),expression(S^'+')),lty=c(1,1),lwd=2,col=c('blue','purple'))}

#Plot histogram with cutoffs shown and normal distributions shown
{hist(antibody1, prob = TRUE, breaks=50, main = paste(antigen, "FMM"), 
  xlab="Normalized Log2(MFI Ratio)", cex.main=0.9, cex.lab=0.8, 
  cex.axis = 0.8, xlim=c(-4,9), ylim = c(0,0.5))
curve(dnorm(x, fit.ab2$mu[1], fit.ab2$sigma[1]), add=TRUE, col="darkblue", lwd=2)
curve(dnorm(x, fit.ab2$mu[2], fit.ab2$sigma[2]), add=TRUE, col="darkblue", lwd=2)
abline(v = multcutoffs[i,4:5], col = "red", lty = 2, lwd = 0.7, xpd=FALSE)}

remove(antigen, antibody1, cutoff, cutoff2, neg, pos, indet, fit.ab2)
```

12 - EBV.EBNA.1 - don't think FMM working that well, perhaps add to the positive one population list
```{r}
i = 12
#Select antigen
antigen <- multantnames[i]
antigen

#subset data for this antigen
singleant <- c(as.matrix(multants[i, (ncol(targetupdate)+1):ncol(multants)]))
#singleant <- singleant[singleant >= 0]

#put the data in numerical order - required to generate probability classification plot below
antibody1 <- sort(singleant)

#### Try FMM model first

fit.ab2<-normalmixEM(antibody1, lambda = c(0.5, 0.5), k = 2, fast=FALSE,maxit=10000,epsilon = 1e-16,maxrestarts=1000)

#5 Plot Cut off Value
summary(fit.ab2)

#cutoff below which is negative - manually set interval end points
cutoff<-uniroot(f,c(0,5),prob=0.90,lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=1)$root

#cutoff above which is positive - manually set interval end points
cutoff2<-uniroot(f2,c(5,10),prob=0.90, lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=2)$root

multcutoffs[i,4] <- cutoff
multcutoffs[i,5] <- cutoff2

#percentage positive 
pos <- sum(antibody1>cutoff2)/length(antibody1) * 100

#percentage negative
neg <- sum(antibody1<cutoff)/length(antibody1) * 100

#percentage indeterminate
indet <- (1-sum(antibody1>cutoff2)/length(antibody1)-sum(antibody1<cutoff)/length(antibody1)) *100

multprevalence[i,5] <- neg
multprevalence[i,6] <- pos
multprevalence[i,7] <- indet

#Plot cutoffs if there are two
{plot(antibody1,fit.ab2$posterior[,1],type='n',xlim=c(-4,10),lwd=2,ylim=c(0,1),col='green',las=1,xlab='Log2(MFI Ratio)',ylab='classification probability', main = paste(antigen, "FMM"))

rect(cutoff,-0.04,cutoff2,1.04,col='light grey',lwd=1.5)
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='red')

abline(h=0.90,lwd=1.5,lty=2)
abline(v=cutoff,lwd=1)
abline(v=cutoff2,lwd=1)

lines(antibody1,fit.ab2$posterior[,1],lwd=2,col='blue')
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='purple')
legend(1125,0.8,c(expression(S^'-'),expression(S^'+')),lty=c(1,1),lwd=2,col=c('blue','purple'))}

#Plot histogram with cutoffs shown and normal distributions shown
{hist(antibody1, prob = TRUE, breaks=50, main = paste(antigen, "FMM"), 
  xlab="Normalized Log2(MFI Ratio)", cex.main=0.9, cex.lab=0.8, 
  cex.axis = 0.8, xlim=c(-2,10), ylim = c(0,0.5))
curve(dnorm(x, fit.ab2$mu[1], fit.ab2$sigma[1]), add=TRUE, col="darkblue", lwd=2)
curve(dnorm(x, fit.ab2$mu[2], fit.ab2$sigma[2]), add=TRUE, col="darkblue", lwd=2)
abline(v = multcutoffs[i,4:5], col = "red", lty = 2, lwd = 0.7, xpd=FALSE)}

remove(antigen, antibody1, cutoff, cutoff2, neg, pos, indet, fit.ab2)
```

13 - EBV.VCA.P18
```{r}
i = 13
#Select antigen
antigen <- multantnames[i]
antigen

#subset data for this antigen
singleant <- c(as.matrix(multants[i, (ncol(targetupdate)+1):ncol(multants)]))
#singleant <- singleant[singleant >= 0]

#put the data in numerical order - required to generate probability classification plot below
antibody1 <- sort(singleant)

#### Try FMM model first

fit.ab2<-normalmixEM(antibody1, lambda = c(0.5, 0.5), k = 2, fast=FALSE,maxit=10000,epsilon = 1e-16,maxrestarts=1000)

#5 Plot Cut off Value
summary(fit.ab2)

#cutoff below which is negative - manually set interval end points
cutoff<-uniroot(f,c(0,4),prob=0.90,lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=1)$root

#cutoff above which is positive - manually set interval end points
cutoff2<-uniroot(f2,c(4,8),prob=0.90, lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=2)$root

multcutoffs[i,4] <- cutoff
multcutoffs[i,5] <- cutoff2

#percentage positive 
pos <- sum(antibody1>cutoff2)/length(antibody1) * 100

#percentage negative
neg <- sum(antibody1<cutoff)/length(antibody1) * 100

#percentage indeterminate
indet <- (1-sum(antibody1>cutoff2)/length(antibody1)-sum(antibody1<cutoff)/length(antibody1)) *100

multprevalence[i,5] <- neg
multprevalence[i,6] <- pos
multprevalence[i,7] <- indet

#Plot cutoffs if there are two
{plot(antibody1,fit.ab2$posterior[,1],type='n',xlim=c(-4,10),lwd=2,ylim=c(0,1),col='green',las=1,xlab='Log2(MFI Ratio)',ylab='classification probability', main = paste(antigen, "FMM"))

rect(cutoff,-0.04,cutoff2,1.04,col='light grey',lwd=1.5)
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='red')

abline(h=0.90,lwd=1.5,lty=2)
abline(v=cutoff,lwd=1)
abline(v=cutoff2,lwd=1)

lines(antibody1,fit.ab2$posterior[,1],lwd=2,col='blue')
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='purple')
legend(1125,0.8,c(expression(S^'-'),expression(S^'+')),lty=c(1,1),lwd=2,col=c('blue','purple'))}

#Plot histogram with cutoffs shown and normal distributions shown
{hist(antibody1, prob = TRUE, breaks=50, main = paste(antigen, "FMM"), 
  xlab="Normalized Log2(MFI Ratio)", cex.main=0.9, cex.lab=0.8, 
  cex.axis = 0.8, xlim=c(-2,10), ylim = c(0,0.5))
curve(dnorm(x, fit.ab2$mu[1], fit.ab2$sigma[1]), add=TRUE, col="darkblue", lwd=2)
curve(dnorm(x, fit.ab2$mu[2], fit.ab2$sigma[2]), add=TRUE, col="darkblue", lwd=2)
abline(v = multcutoffs[i,4:5], col = "red", lty = 2, lwd = 0.7, xpd=FALSE)}

remove(antigen, antibody1, cutoff, cutoff2, neg, pos, indet, fit.ab2)
```

14 - EBV.Whole - negative probability never reaches 0.9, also this antigen did not really work and have better antigens above, will probably remove from analysis
```{r}
i = 14
#Select antigen
antigen <- multantnames[i]
antigen

#subset data for this antigen
singleant <- c(as.matrix(multants[i, (ncol(targetupdate)+1):ncol(multants)]))
#singleant <- singleant[singleant >= 0]

#put the data in numerical order - required to generate probability classification plot below
antibody1 <- sort(singleant)

#### Try FMM model first

fit.ab2<-normalmixEM(antibody1, lambda = c(0.5, 0.5), k = 2, fast=FALSE,maxit=10000,epsilon = 1e-16,maxrestarts=1000)

#5 Plot Cut off Value
summary(fit.ab2)

#cutoff below which is negative - manually set interval end points
#cutoff<-uniroot(f,c(-2,0),prob=0.90,lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=1)$root

#cutoff above which is positive - manually set interval end points
cutoff2<-uniroot(f2,c(0,2),prob=0.90, lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=2)$root

#multcutoffs[i,4] <- cutoff
multcutoffs[i,5] <- cutoff2

#percentage positive 
pos <- sum(antibody1>cutoff2)/length(antibody1) * 100

#percentage negative
#neg <- sum(antibody1<cutoff)/length(antibody1) * 100

#percentage indeterminate
#indet <- (1-sum(antibody1>cutoff2)/length(antibody1)-sum(antibody1<cutoff)/length(antibody1)) *100

#multprevalence[i,5] <- neg
multprevalence[i,6] <- pos
#multprevalence[i,7] <- indet

#Plot cutoffs if there are two
{plot(antibody1,fit.ab2$posterior[,1],type='n',xlim=c(-4,10),lwd=2,ylim=c(0,1),col='green',las=1,xlab='Log2(MFI Ratio)',ylab='classification probability', main = paste(antigen, "FMM"))

#rect(cutoff,-0.04,cutoff2,1.04,col='light grey',lwd=1.5)
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='red')

abline(h=0.90,lwd=1.5,lty=2)
#abline(v=cutoff,lwd=1)
abline(v=cutoff2,lwd=1)

lines(antibody1,fit.ab2$posterior[,1],lwd=2,col='blue')
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='purple')
legend(1125,0.8,c(expression(S^'-'),expression(S^'+')),lty=c(1,1),lwd=2,col=c('blue','purple'))}

#Plot histogram with cutoffs shown and normal distributions shown
{hist(antibody1, prob = TRUE, breaks=50, main = paste(antigen, "FMM"), 
  xlab="Normalized Log2(MFI Ratio)", cex.main=0.9, cex.lab=0.8, 
  cex.axis = 0.8, xlim=c(-2,10), ylim = c(0,2.4))
curve(dnorm(x, fit.ab2$mu[1], fit.ab2$sigma[1]), add=TRUE, col="darkblue", lwd=2)
curve(dnorm(x, fit.ab2$mu[2], fit.ab2$sigma[2]), add=TRUE, col="darkblue", lwd=2)
abline(v = multcutoffs[i,5], col = "red", lty = 2, lwd = 0.7, xpd=FALSE)}
```

15 - Etramp.4.Ag.2 - fmm did work well but may be better using PHE as negs for malarial antigens, same problem happening as above where looks like FMM picking out the two country populations rather than seropositive and seronegative
```{r}
i = 15
#Select antigen
antigen <- multantnames[i]
antigen

#subset data for this antigen
singleant <- c(as.matrix(multants[i, (ncol(targetupdate)+1):ncol(multants)]))
#singleant <- singleant[singleant >= 0]

#put the data in numerical order - required to generate probability classification plot below
antibody1 <- sort(singleant)

#### Try FMM model first

fit.ab2<-normalmixEM(antibody1, lambda = c(0.5, 0.5), k = 2, fast=FALSE,maxit=10000,epsilon = 1e-16,maxrestarts=1000)

#5 Plot Cut off Value
summary(fit.ab2)

#cutoff below which is negative - manually set interval end points
cutoff<-uniroot(f,c(-2,1),prob=0.90,lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=1)$root

#cutoff above which is positive - manually set interval end points
cutoff2<-uniroot(f2,c(1,8),prob=0.90, lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=2)$root

multcutoffs[i,4] <- cutoff
multcutoffs[i,5] <- cutoff2

#percentage positive 
pos <- sum(antibody1>cutoff2)/length(antibody1) * 100

#percentage negative
neg <- sum(antibody1<cutoff)/length(antibody1) * 100

#percentage indeterminate
indet <- (1-sum(antibody1>cutoff2)/length(antibody1)-sum(antibody1<cutoff)/length(antibody1)) *100

multprevalence[i,5] <- neg
multprevalence[i,6] <- pos
multprevalence[i,7] <- indet

#Plot cutoffs if there are two
{plot(antibody1,fit.ab2$posterior[,1],type='n',xlim=c(-4,10),lwd=2,ylim=c(0,1),col='green',las=1,xlab='Log2(MFI Ratio)',ylab='classification probability', main = paste(antigen, "FMM"))

rect(cutoff,-0.04,cutoff2,1.04,col='light grey',lwd=1.5)
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='red')

abline(h=0.90,lwd=1.5,lty=2)
abline(v=cutoff,lwd=1)
abline(v=cutoff2,lwd=1)

lines(antibody1,fit.ab2$posterior[,1],lwd=2,col='blue')
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='purple')
legend(1125,0.8,c(expression(S^'-'),expression(S^'+')),lty=c(1,1),lwd=2,col=c('blue','purple'))}

#Plot histogram with cutoffs shown and normal distributions shown
{hist(antibody1, prob = TRUE, breaks=50, main = paste(antigen, "FMM"), 
  xlab="Normalized Log2(MFI Ratio)", cex.main=0.9, cex.lab=0.8, 
  cex.axis = 0.8, xlim=c(-4,10), ylim = c(0,0.5))
curve(dnorm(x, fit.ab2$mu[1], fit.ab2$sigma[1]), add=TRUE, col="darkblue", lwd=2)
curve(dnorm(x, fit.ab2$mu[2], fit.ab2$sigma[2]), add=TRUE, col="darkblue", lwd=2)
abline(v = multcutoffs[i,4:5], col = "red", lty = 2, lwd = 0.7, xpd=FALSE)}

remove(antigen, antibody1, cutoff, cutoff2, neg, pos, indet, fit.ab2)
```

16 - EXP3 - negative never reaches probability 0.9; country distrubutions match FMM results; maybe use UK population as negatives.

```{r}
i = 16
#Select antigen
antigen <- multantnames[i]
antigen

#subset data for this antigen
singleant <- c(as.matrix(multants[i, (ncol(targetupdate)+1):ncol(multants)]))
#singleant <- singleant[singleant >= 0]

#put the data in numerical order - required to generate probability classification plot below
antibody1 <- sort(singleant)

#### Try FMM model first

fit.ab2<-normalmixEM(antibody1, lambda = c(0.5, 0.5), k = 2, fast=FALSE,maxit=10000,epsilon = 1e-16,maxrestarts=1000)

#5 Plot Cut off Value
summary(fit.ab2)

#cutoff below which is negative - manually set interval end points
#cutoff<-uniroot(f,c(-4,0),prob=0.90,lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=1)$root

#cutoff above which is positive - manually set interval end points
cutoff2<-uniroot(f2,c(0,4),prob=0.90, lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=2)$root

#multcutoffs[i,4] <- cutoff
multcutoffs[i,5] <- cutoff2

#percentage positive 
pos <- sum(antibody1>cutoff2)/length(antibody1) * 100

#percentage negative
#neg <- sum(antibody1<cutoff)/length(antibody1) * 100

#percentage indeterminate
#indet <- (1-sum(antibody1>cutoff2)/length(antibody1)-sum(antibody1<cutoff)/length(antibody1)) *100

#multprevalence[i,5] <- neg
multprevalence[i,6] <- pos
#multprevalence[i,7] <- indet

#Plot cutoffs if there are two
{plot(antibody1,fit.ab2$posterior[,1],type='n',xlim=c(-4,10),lwd=2,ylim=c(0,1),col='green',las=1,xlab='Log2(MFI Ratio)',ylab='classification probability', main = paste(antigen, "FMM"))

#rect(cutoff,-0.04,cutoff2,1.04,col='light grey',lwd=1.5)
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='red')

abline(h=0.90,lwd=1.5,lty=2)
#abline(v=cutoff,lwd=1)
abline(v=cutoff2,lwd=1)

lines(antibody1,fit.ab2$posterior[,1],lwd=2,col='blue')
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='purple')
legend(1125,0.8,c(expression(S^'-'),expression(S^'+')),lty=c(1,1),lwd=2,col=c('blue','purple'))}

#Plot histogram with cutoffs shown and normal distributions shown
{hist(antibody1, prob = TRUE, breaks=50, main = paste(antigen, "FMM"), 
  xlab="Normalized Log2(MFI Ratio)", cex.main=0.9, cex.lab=0.8, 
  cex.axis = 0.8, xlim=c(-4,9), ylim = c(0,0.7))
curve(dnorm(x, fit.ab2$mu[1], fit.ab2$sigma[1]), add=TRUE, col="darkblue", lwd=2)
curve(dnorm(x, fit.ab2$mu[2], fit.ab2$sigma[2]), add=TRUE, col="darkblue", lwd=2)
abline(v = multcutoffs[i,5], col = "red", lty = 2, lwd = 0.7, xpd=FALSE)}

remove(antigen, antibody1, cutoff, cutoff2, neg, pos, indet, fit.ab2)
```

17 - HBV.sAg - negative population never reaches probability 0.9. Looks like a candidate for three populations. 
```{r}
i = 17
#Select antigen
antigen <- multantnames[i]
antigen

#subset data for this antigen
singleant <- c(as.matrix(multants[i, (ncol(targetupdate)+1):ncol(multants)]))
#singleant <- singleant[singleant >= 0]

#put the data in numerical order - required to generate probability classification plot below
antibody1 <- sort(singleant)

#### Try FMM model first

fit.ab2<-normalmixEM(antibody1, lambda = c(0.5, 0.5), k = 2, fast=FALSE,maxit=10000,epsilon = 1e-16,maxrestarts=1000)

#5 Plot Cut off Value
summary(fit.ab2)

#cutoff below which is negative - manually set interval end points
#cutoff<-uniroot(f,c(-6,.8),prob=0.90,lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=1)$root

#cutoff above which is positive - manually set interval end points
cutoff2<-uniroot(f2,c(1,8),prob=0.90, lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=2)$root

#multcutoffs[i,4] <- cutoff
multcutoffs[i,5] <- cutoff2

#percentage positive 
pos <- sum(antibody1>cutoff2)/length(antibody1) * 100

#percentage negative
#neg <- sum(antibody1<cutoff)/length(antibody1) * 100

#percentage indeterminate
#indet <- (1-sum(antibody1>cutoff2)/length(antibody1)-sum(antibody1<cutoff)/length(antibody1)) *100

#multprevalence[i,5] <- neg
multprevalence[i,6] <- pos
#multprevalence[i,7] <- indet

#Plot cutoffs if there are two
{plot(antibody1,fit.ab2$posterior[,1],type='n',xlim=c(-4,10),lwd=2,ylim=c(0,1),col='green',las=1,xlab='Log2(MFI Ratio)',ylab='classification probability', main = paste(antigen, "FMM"))

#rect(cutoff,-0.04,cutoff2,1.04,col='light grey',lwd=1.5)
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='red')

abline(h=0.90,lwd=1.5,lty=2)
#abline(v=cutoff,lwd=1)
abline(v=cutoff2,lwd=1)

lines(antibody1,fit.ab2$posterior[,1],lwd=2,col='blue')
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='purple')
legend(1125,0.8,c(expression(S^'-'),expression(S^'+')),lty=c(1,1),lwd=2,col=c('blue','purple'))}

#Plot histogram with cutoffs shown and normal distributions shown
{hist(antibody1, prob = TRUE, breaks=50, main = paste(antigen, "FMM"), 
  xlab="Normalized Log2(MFI Ratio)", cex.main=0.9, cex.lab=0.8, 
  cex.axis = 0.8, xlim=c(-4,10), ylim = c(0,0.5))
curve(dnorm(x, fit.ab2$mu[1], fit.ab2$sigma[1]), add=TRUE, col="darkblue", lwd=2)
curve(dnorm(x, fit.ab2$mu[2], fit.ab2$sigma[2]), add=TRUE, col="darkblue", lwd=2)
abline(v = multcutoffs[i,5], col = "red", lty = 2, lwd = 0.7, xpd=FALSE)}

remove(antigen, antibody1, cutoff, cutoff2, neg, pos, indet, fit.ab2)
```

18 - HSV1 - negative population never reaches 0.9 ; could possible be three populations. 
```{r}
i = 18
#Select antigen
antigen <- multantnames[i]
antigen

#subset data for this antigen
singleant <- c(as.matrix(multants[i, (ncol(targetupdate)+1):ncol(multants)]))
#singleant <- singleant[singleant >= 0]

#put the data in numerical order - required to generate probability classification plot below
antibody1 <- sort(singleant)

#### Try FMM model first

fit.ab2<-normalmixEM(antibody1, lambda = c(0.5, 0.5), k = 2, mu = c(-0.0709852, 1.257015), sigma = c(0.1537635, 0.589298),fast=FALSE,maxit=10000,epsilon = 1e-16,maxrestarts=1000)

#5 Plot Cut off Value
summary(fit.ab2)

#cutoff below which is negative - manually set interval end points
#cutoff<-uniroot(f,c(-0.5,0.2),prob=0.90,lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=1)$root

#cutoff above which is positive - manually set interval end points
cutoff2<-uniroot(f2,c(0,8),prob=0.90, lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=2)$root

#multcutoffs[i,4] <- cutoff
multcutoffs[i,5] <- cutoff2

#percentage positive 
pos <- sum(antibody1>cutoff2)/length(antibody1) * 100

#percentage negative
#neg <- sum(antibody1<cutoff)/length(antibody1) * 100

#percentage indeterminate
#indet <- (1-sum(antibody1>cutoff2)/length(antibody1)-sum(antibody1<cutoff)/length(antibody1)) *100

#multprevalence[i,5] <- neg
multprevalence[i,6] <- pos
#multprevalence[i,7] <- indet

#Plot cutoffs if there are two
{plot(antibody1,fit.ab2$posterior[,1],type='n',xlim=c(-4,10),lwd=2,ylim=c(0,1),col='green',las=1,xlab='Log2(MFI Ratio)',ylab='classification probability', main = paste(antigen, "FMM"))

#rect(cutoff,-0.04,cutoff2,1.04,col='light grey',lwd=1.5)
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='red')

abline(h=0.90,lwd=1.5,lty=2)
#abline(v=cutoff,lwd=1)
abline(v=cutoff2,lwd=1)

lines(antibody1,fit.ab2$posterior[,1],lwd=2,col='blue')
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='purple')
legend(1125,0.8,c(expression(S^'-'),expression(S^'+')),lty=c(1,1),lwd=2,col=c('blue','purple'))}

#Plot histogram with cutoffs shown and normal distributions shown
{hist(antibody1, prob = TRUE, breaks=50, main = paste(antigen, "FMM"), 
  xlab="Normalized Log2(MFI Ratio)", cex.main=0.9, cex.lab=0.8, 
  cex.axis = 0.8, xlim=c(-2,8), ylim = c(0,1))
curve(dnorm(x, fit.ab2$mu[1], fit.ab2$sigma[1]), add=TRUE, col="darkblue", lwd=2)
curve(dnorm(x, fit.ab2$mu[2], fit.ab2$sigma[2]), add=TRUE, col="darkblue", lwd=2)
abline(v = multcutoffs[i,5], col = "red", lty = 2, lwd = 0.7, xpd=FALSE)}

remove(antigen, antibody1, cutoff, cutoff2, neg, pos, indet, fit.ab2)
```

19 - HSV2 - negative population never reaches probability 0.9
```{r}
i = 19
#Select antigen
antigen <- multantnames[i]
antigen

#subset data for this antigen
singleant <- c(as.matrix(multants[i, (ncol(targetupdate)+1):ncol(multants)]))
#singleant <- singleant[singleant >= 0]

#put the data in numerical order - required to generate probability classification plot below
antibody1 <- sort(singleant)

#### Try FMM model first

#this time, both different FMM solutions were not matching the negative and positive populations I see from my country and overall histograms, but when I put in mu = c(0,1), sigma = c(0.2,0.5) I was able to get a solution that matches those populations. 
fit.ab2<-normalmixEM(antibody1, lambda = c(0.5, 0.5), k = 2, mu = c(0.0279830, 1.050985), sigma = c(0.1023426, 0.619804), fast=FALSE,maxit=10000,epsilon = 1e-16,maxrestarts=1000)

#5 Plot Cut off Value
summary(fit.ab2)

#cutoff below which is negative - manually set interval end points
#cutoff<-uniroot(f,c(-1,0.5),prob=0.90,lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=1)$root

#cutoff above which is positive - manually set interval end points
cutoff2<-uniroot(f2,c(0,2),prob=0.90, lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=2)$root

#multcutoffs[i,4] <- cutoff
multcutoffs[i,5] <- cutoff2

#percentage positive 
pos <- sum(antibody1>cutoff2)/length(antibody1) * 100

#percentage negative
#neg <- sum(antibody1<cutoff)/length(antibody1) * 100

#percentage indeterminate
#indet <- (1-sum(antibody1>cutoff2)/length(antibody1)-sum(antibody1<cutoff)/length(antibody1)) *100

#multprevalence[i,5] <- neg
multprevalence[i,6] <- pos
#multprevalence[i,7] <- indet

#Plot cutoffs if there are two
{plot(antibody1,fit.ab2$posterior[,1],type='n',xlim=c(-4,10),lwd=2,ylim=c(0,1),col='green',las=1,xlab='Log2(MFI Ratio)',ylab='classification probability', main = paste(antigen, "FMM"))

#rect(cutoff,-0.04,cutoff2,1.04,col='light grey',lwd=1.5)
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='red')

abline(h=0.90,lwd=1.5,lty=2)
#abline(v=cutoff,lwd=1)
abline(v=cutoff2,lwd=1)

lines(antibody1,fit.ab2$posterior[,1],lwd=2,col='blue')
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='purple')
legend(1125,0.8,c(expression(S^'-'),expression(S^'+')),lty=c(1,1),lwd=2,col=c('blue','purple'))}

#Plot histogram with cutoffs shown and normal distributions shown
{hist(antibody1, prob = TRUE, breaks=50, main = paste(antigen, "FMM"), 
  xlab="Normalized Log2(MFI Ratio)", cex.main=0.9, cex.lab=0.8, 
  cex.axis = 0.8, xlim=c(-2,8), ylim = c(0,1.5))
curve(dnorm(x, fit.ab2$mu[1], fit.ab2$sigma[1]), add=TRUE, col="darkblue", lwd=2)
curve(dnorm(x, fit.ab2$mu[2], fit.ab2$sigma[2]), add=TRUE, col="darkblue", lwd=2)
abline(v = multcutoffs[i,5], col = "red", lty = 2, lwd = 0.7, xpd=FALSE)}

remove(antigen, antibody1, cutoff, cutoff2, neg, pos, indet, fit.ab2)
```


20 - Influenza.B - negative population never reaches probability of 0.9
```{r}
i = 20
#Select antigen
antigen <- multantnames[i]
antigen

#subset data for this antigen
singleant <- c(as.matrix(multants[i, (ncol(targetupdate)+1):ncol(multants)]))
#singleant <- singleant[singleant >= 0]

#put the data in numerical order - required to generate probability classification plot below
antibody1 <- sort(singleant)

#### Try FMM model first

fit.ab2<-normalmixEM(antibody1, lambda = c(0.5, 0.5), k = 2,mu = c(1.886046, 3.720201), sigma = c(0.801257, 0.657361), fast=FALSE,maxit=10000,epsilon = 1e-16,maxrestarts=1000)

#5 Plot Cut off Value
summary(fit.ab2)

#cutoff below which is negative - manually set interval end points
cutoff<-uniroot(f,c(-1,3),prob=0.90,lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=1)$root

#cutoff above which is positive - manually set interval end points
cutoff2<-uniroot(f2,c(2,8),prob=0.90, lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=2)$root

multcutoffs[i,4] <- cutoff
multcutoffs[i,5] <- cutoff2

#percentage positive 
pos <- sum(antibody1>cutoff2)/length(antibody1) * 100

#percentage negative
neg <- sum(antibody1<cutoff)/length(antibody1) * 100

#percentage indeterminate
indet <- (1-sum(antibody1>cutoff2)/length(antibody1)-sum(antibody1<cutoff)/length(antibody1)) *100

multprevalence[i,5] <- neg
multprevalence[i,6] <- pos
multprevalence[i,7] <- indet

#Plot cutoffs if there are two
{plot(antibody1,fit.ab2$posterior[,1],type='n',xlim=c(-4,10),lwd=2,ylim=c(0,1),col='green',las=1,xlab='Log2(MFI Ratio)',ylab='classification probability', main = paste(antigen, "FMM"))

rect(cutoff,-0.04,cutoff2,1.04,col='light grey',lwd=1.5)
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='red')

abline(h=0.90,lwd=1.5,lty=2)
abline(v=cutoff,lwd=1)
abline(v=cutoff2,lwd=1)

lines(antibody1,fit.ab2$posterior[,1],lwd=2,col='blue')
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='purple')
legend(1125,0.8,c(expression(S^'-'),expression(S^'+')),lty=c(1,1),lwd=2,col=c('blue','purple'))}

#Plot histogram with cutoffs shown and normal distributions shown
{hist(antibody1, prob = TRUE, breaks=50, main = paste(antigen, "FMM"), 
  xlab="Normalized Log2(MFI Ratio)", cex.main=0.9, cex.lab=0.8, 
  cex.axis = 0.8, xlim=c(-2,9), ylim = c(0,0.7))
curve(dnorm(x, fit.ab2$mu[1], fit.ab2$sigma[1]), add=TRUE, col="darkblue", lwd=2)
curve(dnorm(x, fit.ab2$mu[2], fit.ab2$sigma[2]), add=TRUE, col="darkblue", lwd=2)
abline(v = multcutoffs[i,4:5], col = "red", lty = 2, lwd = 0.7, xpd=FALSE)}

remove(antigen, antibody1, cutoff, cutoff2, neg, pos, indet, fit.ab2)

```

21 - Meningococcal.Y - works well as two populations but looks like could also work well as three
```{r}
i = 21
#Select antigen
antigen <- multantnames[i]
antigen

#subset data for this antigen
singleant <- c(as.matrix(multants[i, (ncol(targetupdate)+1):ncol(multants)]))
#singleant <- singleant[singleant >= 0]

#put the data in numerical order - required to generate probability classification plot below
antibody1 <- sort(singleant)

#### Try FMM model first

fit.ab2<-normalmixEM(antibody1, lambda = c(0.5, 0.5), k = 2, fast=FALSE,maxit=10000,epsilon = 1e-16,maxrestarts=1000)

#5 Plot Cut off Value
summary(fit.ab2)

#cutoff below which is negative - manually set interval end points
cutoff<-uniroot(f,c(0,2),prob=0.90,lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=1)$root

#cutoff above which is positive - manually set interval end points
cutoff2<-uniroot(f2,c(1,8),prob=0.90, lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=2)$root

multcutoffs[i,4] <- cutoff
multcutoffs[i,5] <- cutoff2

#percentage positive 
pos <- sum(antibody1>cutoff2)/length(antibody1) * 100

#percentage negative
neg <- sum(antibody1<cutoff)/length(antibody1) * 100

#percentage indeterminate
indet <- (1-sum(antibody1>cutoff2)/length(antibody1)-sum(antibody1<cutoff)/length(antibody1)) *100

multprevalence[i,5] <- neg
multprevalence[i,6] <- pos
multprevalence[i,7] <- indet

#Plot cutoffs if there are two
{plot(antibody1,fit.ab2$posterior[,1],type='n',xlim=c(-4,10),lwd=2,ylim=c(0,1),col='green',las=1,xlab='Log2(MFI Ratio)',ylab='classification probability', main = paste(antigen, "FMM"))

rect(cutoff,-0.04,cutoff2,1.04,col='light grey',lwd=1.5)
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='red')

abline(h=0.90,lwd=1.5,lty=2)
abline(v=cutoff,lwd=1)
abline(v=cutoff2,lwd=1)

lines(antibody1,fit.ab2$posterior[,1],lwd=2,col='blue')
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='purple')
legend(1125,0.8,c(expression(S^'-'),expression(S^'+')),lty=c(1,1),lwd=2,col=c('blue','purple'))}

#Plot histogram with cutoffs shown and normal distributions shown
{hist(antibody1, prob = TRUE, breaks=50, main = paste(antigen, "FMM"), 
  xlab="Normalized Log2(MFI Ratio)", cex.main=0.9, cex.lab=0.8, 
  cex.axis = 0.8, xlim=c(-2,9), ylim = c(0,0.7))
curve(dnorm(x, fit.ab2$mu[1], fit.ab2$sigma[1]), add=TRUE, col="darkblue", lwd=2)
curve(dnorm(x, fit.ab2$mu[2], fit.ab2$sigma[2]), add=TRUE, col="darkblue", lwd=2)
abline(v = multcutoffs[i,4:5], col = "red", lty = 2, lwd = 0.7, xpd=FALSE)}

remove(antigen, antibody1, cutoff, cutoff2, neg, pos, indet, fit.ab2)
```

22 - MSP1.19 - the plot looks like may be 3 populations but doesn't make sense based on the UK density plot. Once again, malarial antigen, may be better to use UK as negatives and do mean +/- 3SD.
```{r}
i = 22
#Select antigen
antigen <- multantnames[i]
antigen

#subset data for this antigen
singleant <- c(as.matrix(multants[i, (ncol(targetupdate)+1):ncol(multants)]))
#singleant <- singleant[singleant >= 0]

#put the data in numerical order - required to generate probability classification plot below
antibody1 <- sort(singleant)

#### Try FMM model first

#FMM had several solutions and sometimes did not converge. To select a solution, had to put in lambda, mu, and sigma!!
fit.ab2<-normalmixEM(antibody1, lambda =c(0.194031, 0.805969), k = 2,mu = c(5.031505, 0.973021),sigma=c(1.582342, 1.859804), fast=FALSE,maxit=10000,epsilon = 1e-16,maxrestarts=1000)

#5 Plot Cut off Value
summary(fit.ab2)

#cutoff below which is negative - manually set interval end points
cutoff<-uniroot(f,c(0,4),prob=0.90,lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=1)$root

#cutoff above which is positive - manually set interval end points
cutoff2<-uniroot(f2,c(1,8),prob=0.90, lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=2)$root

multcutoffs[i,4] <- cutoff
multcutoffs[i,5] <- cutoff2

#percentage positive 
pos <- sum(antibody1>cutoff2)/length(antibody1) * 100

#percentage negative
neg <- sum(antibody1<cutoff)/length(antibody1) * 100

#percentage indeterminate
indet <- (1-sum(antibody1>cutoff2)/length(antibody1)-sum(antibody1<cutoff)/length(antibody1)) *100

multprevalence[i,5] <- neg
multprevalence[i,6] <- pos
multprevalence[i,7] <- indet

#Plot cutoffs if there are two
{plot(antibody1,fit.ab2$posterior[,1],type='n',xlim=c(-4,10),lwd=2,ylim=c(0,1),col='green',las=1,xlab='Log2(MFI Ratio)',ylab='classification probability', main = paste(antigen, "FMM"))

rect(cutoff,-0.04,cutoff2,1.04,col='light grey',lwd=1.5)
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='red')

abline(h=0.90,lwd=1.5,lty=2)
abline(v=cutoff,lwd=1)
abline(v=cutoff2,lwd=1)

lines(antibody1,fit.ab2$posterior[,1],lwd=2,col='blue')
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='purple')
legend(1125,0.8,c(expression(S^'-'),expression(S^'+')),lty=c(1,1),lwd=2,col=c('blue','purple'))}

#Plot histogram with cutoffs shown and normal distributions shown
{hist(antibody1, prob = TRUE, breaks=50, main = paste(antigen, "FMM"), 
  xlab="Normalized Log2(MFI Ratio)", cex.main=0.9, cex.lab=0.8, 
  cex.axis = 0.8, xlim=c(-4,10), ylim = c(0,0.5))
curve(dnorm(x, fit.ab2$mu[1], fit.ab2$sigma[1]), add=TRUE, col="darkblue", lwd=2)
curve(dnorm(x, fit.ab2$mu[2], fit.ab2$sigma[2]), add=TRUE, col="darkblue", lwd=2)
abline(v = multcutoffs[i,4:5], col = "red", lty = 2, lwd = 0.7, xpd=FALSE)}

remove(antigen, antibody1, cutoff, cutoff2, neg, pos, indet, fit.ab2)
```

23 - Mtb.Acr.HspX.
```{r}
i = 23
#Select antigen
antigen <- multantnames[i]
antigen

#subset data for this antigen
singleant <- c(as.matrix(multants[i, (ncol(targetupdate)+1):ncol(multants)]))
#singleant <- singleant[singleant >= 0]

#put the data in numerical order - required to generate probability classification plot below
antibody1 <- sort(singleant)

#### Try FMM model first

#FMM had several solutions and sometimes did not converge. To select a solution, had to put in lambda, mu, and sigma!!
fit.ab2<-normalmixEM(antibody1, lambda =c(0.5, 0.5), k = 2, fast=FALSE,maxit=10000,epsilon = 1e-16,maxrestarts=1000)

#5 Plot Cut off Value
summary(fit.ab2)

#cutoff below which is negative - manually set interval end points
cutoff<-uniroot(f,c(0.1,1),prob=0.90,lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=1)$root

#cutoff above which is positive - manually set interval end points
cutoff2<-uniroot(f2,c(1,8),prob=0.90, lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=2)$root

multcutoffs[i,4] <- cutoff
multcutoffs[i,5] <- cutoff2

#percentage positive 
pos <- sum(antibody1>cutoff2)/length(antibody1) * 100

#percentage negative
neg <- sum(antibody1<cutoff)/length(antibody1) * 100

#percentage indeterminate
indet <- (1-sum(antibody1>cutoff2)/length(antibody1)-sum(antibody1<cutoff)/length(antibody1)) *100

multprevalence[i,5] <- neg
multprevalence[i,6] <- pos
multprevalence[i,7] <- indet

#Plot cutoffs if there are two
{plot(antibody1,fit.ab2$posterior[,1],type='n',xlim=c(-4,10),lwd=2,ylim=c(0,1),col='green',las=1,xlab='Log2(MFI Ratio)',ylab='classification probability', main = paste(antigen, "FMM"))

rect(cutoff,-0.04,cutoff2,1.04,col='light grey',lwd=1.5)
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='red')

abline(h=0.90,lwd=1.5,lty=2)
abline(v=cutoff,lwd=1)
abline(v=cutoff2,lwd=1)

lines(antibody1,fit.ab2$posterior[,1],lwd=2,col='blue')
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='purple')
legend(1125,0.8,c(expression(S^'-'),expression(S^'+')),lty=c(1,1),lwd=2,col=c('blue','purple'))}

#Plot histogram with cutoffs shown and normal distributions shown
{hist(antibody1, prob = TRUE, breaks=50, main = paste(antigen, "FMM"), 
  xlab="Normalized Log2(MFI Ratio)", cex.main=0.9, cex.lab=0.8, 
  cex.axis = 0.8, xlim=c(-2,8), ylim = c(0,1))
curve(dnorm(x, fit.ab2$mu[1], fit.ab2$sigma[1]), add=TRUE, col="darkblue", lwd=2)
curve(dnorm(x, fit.ab2$mu[2], fit.ab2$sigma[2]), add=TRUE, col="darkblue", lwd=2)
abline(v = multcutoffs[i,4:5], col = "red", lty = 2, lwd = 0.7, xpd=FALSE)}

remove(antigen, antibody1, cutoff, cutoff2, neg, pos, indet, fit.ab2)
```
24 - Mtb.Ag85B
```{r}
i = 24
#Select antigen
antigen <- multantnames[i]
antigen

#subset data for this antigen
singleant <- c(as.matrix(multants[i, (ncol(targetupdate)+1):ncol(multants)]))
#singleant <- singleant[singleant >= 0]

#put the data in numerical order - required to generate probability classification plot below
antibody1 <- sort(singleant)

#### Try FMM model first

fit.ab2<-normalmixEM(antibody1, lambda =c(0.5, 0.5), k = 2, fast=FALSE,maxit=10000,epsilon = 1e-16,maxrestarts=1000)

#5 Plot Cut off Value
summary(fit.ab2)

#cutoff below which is negative - manually set interval end points
cutoff<-uniroot(f,c(0,2),prob=0.90,lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=1)$root

#cutoff above which is positive - manually set interval end points
cutoff2<-uniroot(f2,c(1,8),prob=0.90, lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=2)$root

multcutoffs[i,4] <- cutoff
multcutoffs[i,5] <- cutoff2

#percentage positive 
pos <- sum(antibody1>cutoff2)/length(antibody1) * 100

#percentage negative
neg <- sum(antibody1<cutoff)/length(antibody1) * 100

#percentage indeterminate
indet <- (1-sum(antibody1>cutoff2)/length(antibody1)-sum(antibody1<cutoff)/length(antibody1)) *100

multprevalence[i,5] <- neg
multprevalence[i,6] <- pos
multprevalence[i,7] <- indet

#Plot cutoffs if there are two
{plot(antibody1,fit.ab2$posterior[,1],type='n',xlim=c(-4,10),lwd=2,ylim=c(0,1),col='green',las=1,xlab='Log2(MFI Ratio)',ylab='classification probability', main = paste(antigen, "FMM"))

rect(cutoff,-0.04,cutoff2,1.04,col='light grey',lwd=1.5)
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='red')

abline(h=0.90,lwd=1.5,lty=2)
abline(v=cutoff,lwd=1)
abline(v=cutoff2,lwd=1)

lines(antibody1,fit.ab2$posterior[,1],lwd=2,col='blue')
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='purple')
legend(1125,0.8,c(expression(S^'-'),expression(S^'+')),lty=c(1,1),lwd=2,col=c('blue','purple'))}

#Plot histogram with cutoffs shown and normal distributions shown
{hist(antibody1, prob = TRUE, breaks=50, main = paste(antigen, "FMM"), 
  xlab="Normalized Log2(MFI Ratio)", cex.main=0.9, cex.lab=0.8, 
  cex.axis = 0.8, xlim=c(-2,8), ylim = c(0,1))
curve(dnorm(x, fit.ab2$mu[1], fit.ab2$sigma[1]), add=TRUE, col="darkblue", lwd=2)
curve(dnorm(x, fit.ab2$mu[2], fit.ab2$sigma[2]), add=TRUE, col="darkblue", lwd=2)
abline(v = multcutoffs[i,4:5], col = "red", lty = 2, lwd = 0.7, xpd=FALSE)}

remove(antigen, antibody1, cutoff, cutoff2, neg, pos, indet, fit.ab2)
```
25 - Mtb.CFP10.ESAT.6 - negative population never reaches probability of 0.9.
```{r}
i = 25
#Select antigen
antigen <- multantnames[i]
antigen

#subset data for this antigen
singleant <- c(as.matrix(multants[i, (ncol(targetupdate)+1):ncol(multants)]))
#singleant <- singleant[singleant >= 0]

#put the data in numerical order - required to generate probability classification plot below
antibody1 <- sort(singleant)

#### Try FMM model first

fit.ab2<-normalmixEM(antibody1, lambda =c(0.5, 0.5), k = 2, fast=FALSE,maxit=10000,epsilon = 1e-16,maxrestarts=1000)

#5 Plot Cut off Value
summary(fit.ab2)

#cutoff below which is negative - manually set interval end points
#cutoff<-uniroot(f,c(-2,2),prob=0.90,lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=1)$root

#cutoff above which is positive - manually set interval end points
cutoff2<-uniroot(f2,c(1,8),prob=0.90, lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=2)$root

#multcutoffs[i,4] <- cutoff
multcutoffs[i,5] <- cutoff2

#percentage positive 
pos <- sum(antibody1>cutoff2)/length(antibody1) * 100

#percentage negative
#neg <- sum(antibody1<cutoff)/length(antibody1) * 100

#percentage indeterminate
#indet <- (1-sum(antibody1>cutoff2)/length(antibody1)-sum(antibody1<cutoff)/length(antibody1)) *100

#multprevalence[i,5] <- neg
multprevalence[i,6] <- pos
#multprevalence[i,7] <- indet

#Plot cutoffs if there are two
{plot(antibody1,fit.ab2$posterior[,1],type='n',xlim=c(-4,10),lwd=2,ylim=c(0,1),col='green',las=1,xlab='Log2(MFI Ratio)',ylab='classification probability', main = paste(antigen, "FMM"))

#rect(cutoff,-0.04,cutoff2,1.04,col='light grey',lwd=1.5)
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='red')

abline(h=0.90,lwd=1.5,lty=2)
#abline(v=cutoff,lwd=1)
abline(v=cutoff2,lwd=1)

lines(antibody1,fit.ab2$posterior[,1],lwd=2,col='blue')
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='purple')
legend(1125,0.8,c(expression(S^'-'),expression(S^'+')),lty=c(1,1),lwd=2,col=c('blue','purple'))}

#Plot histogram with cutoffs shown and normal distributions shown
{hist(antibody1, prob = TRUE, breaks=50, main = paste(antigen, "FMM"), 
  xlab="Normalized Log2(MFI Ratio)", cex.main=0.9, cex.lab=0.8, 
  cex.axis = 0.8, xlim=c(-2,10), ylim = c(0,0.7))
curve(dnorm(x, fit.ab2$mu[1], fit.ab2$sigma[1]), add=TRUE, col="darkblue", lwd=2)
curve(dnorm(x, fit.ab2$mu[2], fit.ab2$sigma[2]), add=TRUE, col="darkblue", lwd=2)
abline(v = multcutoffs[i,5], col = "red", lty = 2, lwd = 0.7, xpd=FALSE)}

remove(antigen, antibody1, cutoff, cutoff2, neg, pos, indet, fit.ab2)
```

26 - PHISTC.B - negative population never reaches probability of 0.9
```{r}
i = 26
#Select antigen
antigen <- multantnames[i]
antigen

#subset data for this antigen
singleant <- c(as.matrix(multants[i, (ncol(targetupdate)+1):ncol(multants)]))
#singleant <- singleant[singleant >= 0]

#put the data in numerical order - required to generate probability classification plot below
antibody1 <- sort(singleant)

#### Try FMM model first

fit.ab2<-normalmixEM(antibody1, lambda = c(0.5, 0.5), k = 2, fast=FALSE,maxit=10000,epsilon = 1e-16,maxrestarts=1000)

#5 Plot Cut off Value
summary(fit.ab2)

#cutoff below which is negative - manually set interval end points
#cutoff<-uniroot(f,c(-4,0),prob=0.90,lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=1)$root

#cutoff above which is positive - manually set interval end points
cutoff2<-uniroot(f2,c(0,4),prob=0.90, lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=2)$root

#multcutoffs[i,4] <- cutoff
multcutoffs[i,5] <- cutoff2

#percentage positive 
pos <- sum(antibody1>cutoff2)/length(antibody1) * 100

#percentage negative
#neg <- sum(antibody1<cutoff)/length(antibody1) * 100

#percentage indeterminate
#indet <- (1-sum(antibody1>cutoff2)/length(antibody1)-sum(antibody1<cutoff)/length(antibody1)) *100

#multprevalence[i,5] <- neg
multprevalence[i,6] <- pos
#multprevalence[i,7] <- indet

#Plot cutoffs if there are two
{plot(antibody1,fit.ab2$posterior[,1],type='n',xlim=c(-4,10),lwd=2,ylim=c(0,1),col='green',las=1,xlab='Log2(MFI Ratio)',ylab='classification probability', main = paste(antigen, "FMM"))

#rect(cutoff,-0.04,cutoff2,1.04,col='light grey',lwd=1.5)
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='red')

abline(h=0.90,lwd=1.5,lty=2)
#abline(v=cutoff,lwd=1)
abline(v=cutoff2,lwd=1)

lines(antibody1,fit.ab2$posterior[,1],lwd=2,col='blue')
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='purple')
legend(1125,0.8,c(expression(S^'-'),expression(S^'+')),lty=c(1,1),lwd=2,col=c('blue','purple'))}

#Plot histogram with cutoffs shown and normal distributions shown
{hist(antibody1, prob = TRUE, breaks=50, main = paste(antigen, "FMM"), 
  xlab="Normalized Log2(MFI Ratio)", cex.main=0.9, cex.lab=0.8, 
  cex.axis = 0.8, xlim=c(-4,9), ylim = c(0,0.5))
curve(dnorm(x, fit.ab2$mu[1], fit.ab2$sigma[1]), add=TRUE, col="darkblue", lwd=2)
curve(dnorm(x, fit.ab2$mu[2], fit.ab2$sigma[2]), add=TRUE, col="darkblue", lwd=2)
abline(v = multcutoffs[i,5], col = "red", lty = 2, lwd = 0.7, xpd=FALSE)}

remove(antigen, antibody1, cutoff, cutoff2, neg, pos, indet, fit.ab2)
```

27 - Pneumococcal.14 - positive population never reaches probability of 0.9. looks like one positive population from original histogram - need to read more about expected prevalence before any attempts to repeat this. Came up with same solution 11 times but taking almost 10,000 iterations every time which is very unusual.
```{r}
i = 27
#Select antigen
antigen <- multantnames[i]
antigen

#subset data for this antigen
singleant <- c(as.matrix(multants[i, (ncol(targetupdate)+1):ncol(multants)]))
#singleant <- singleant[singleant >= 0]

#put the data in numerical order - required to generate probability classification plot below
antibody1 <- sort(singleant)

#### Try FMM model first

fit.ab2<-normalmixEM(antibody1, lambda = c(0.5, 0.5), k = 2, fast=FALSE,maxit=10000,epsilon = 1e-16,maxrestarts=1000)

#5 Plot Cut off Value
summary(fit.ab2)

#cutoff below which is negative - manually set interval end points
cutoff<-uniroot(f,c(2,5),prob=0.90,lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=1)$root

#cutoff above which is positive - manually set interval end points
#cutoff2<-uniroot(f2,c(1,8),prob=0.90, lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=2)$root

multcutoffs[i,4] <- cutoff
#multcutoffs[i,5] <- cutoff2

#percentage positive 
#pos <- sum(antibody1>cutoff2)/length(antibody1) * 100

#percentage negative
neg <- sum(antibody1<cutoff)/length(antibody1) * 100

#percentage indeterminate
#indet <- (1-sum(antibody1>cutoff2)/length(antibody1)-sum(antibody1<cutoff)/length(antibody1)) *100

multprevalence[i,5] <- neg
#multprevalence[i,6] <- pos
#multprevalence[i,7] <- indet

#Plot cutoffs if there are two
{plot(antibody1,fit.ab2$posterior[,1],type='n',xlim=c(-4,10),lwd=2,ylim=c(0,1),col='green',las=1,xlab='Log2(MFI Ratio)',ylab='classification probability', main = paste(antigen, "FMM"))

#rect(cutoff,-0.04,cutoff2,1.04,col='light grey',lwd=1.5)
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='red')

abline(h=0.90,lwd=1.5,lty=2)
abline(v=cutoff,lwd=1)
#abline(v=cutoff2,lwd=1)

lines(antibody1,fit.ab2$posterior[,1],lwd=2,col='blue')
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='purple')
legend(1125,0.8,c(expression(S^'-'),expression(S^'+')),lty=c(1,1),lwd=2,col=c('blue','purple'))}

#Plot histogram with cutoffs shown and normal distributions shown
{hist(antibody1, prob = TRUE, breaks=50, main = paste(antigen, "FMM"), 
  xlab="Normalized Log2(MFI Ratio)", cex.main=0.9, cex.lab=0.8, 
  cex.axis = 0.8, xlim=c(-4,10), ylim = c(0,0.5))
curve(dnorm(x, fit.ab2$mu[1], fit.ab2$sigma[1]), add=TRUE, col="darkblue", lwd=2)
curve(dnorm(x, fit.ab2$mu[2], fit.ab2$sigma[2]), add=TRUE, col="darkblue", lwd=2)
abline(v = multcutoffs[i,4], col = "red", lty = 2, lwd = 0.7, xpd=FALSE)}

remove(antigen, antibody1, cutoff, cutoff2, neg, pos, indet, fit.ab2)
```

28 - Pneumococcal.18C
```{r}
i = 28
#Select antigen
antigen <- multantnames[i]
antigen

#subset data for this antigen
singleant <- c(as.matrix(multants[i, (ncol(targetupdate)+1):ncol(multants)]))
#singleant <- singleant[singleant >= 0]

#put the data in numerical order - required to generate probability classification plot below
antibody1 <- sort(singleant)

#### Try FMM model first

fit.ab2<-normalmixEM(antibody1, lambda =c(0.288671, 0.711329),mu = c(2.406266, 4.069546),
sigma = c(1.046207, 1.011170), k = 2, fast=FALSE,maxit=10000,epsilon = 1e-16,maxrestarts=1000)

#5 Plot Cut off Value
summary(fit.ab2)

#cutoff below which is negative - manually set interval end points
cutoff<-uniroot(f,c(0,2),prob=0.90,lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=1)$root

#cutoff above which is positive - manually set interval end points
cutoff2<-uniroot(f2,c(2,6),prob=0.90, lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=2)$root

multcutoffs[i,4] <- cutoff
multcutoffs[i,5] <- cutoff2

#percentage positive 
pos <- sum(antibody1>cutoff2)/length(antibody1) * 100

#percentage negative
neg <- sum(antibody1<cutoff)/length(antibody1) * 100

#percentage indeterminate
indet <- (1-sum(antibody1>cutoff2)/length(antibody1)-sum(antibody1<cutoff)/length(antibody1)) *100

multprevalence[i,5] <- neg
multprevalence[i,6] <- pos
multprevalence[i,7] <- indet

#Plot cutoffs if there are two
{plot(antibody1,fit.ab2$posterior[,1],type='n',xlim=c(-4,10),lwd=2,ylim=c(0,1),col='green',las=1,xlab='Log2(MFI Ratio)',ylab='classification probability', main = paste(antigen, "FMM"))

rect(cutoff,-0.04,cutoff2,1.04,col='light grey',lwd=1.5)
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='red')

abline(h=0.90,lwd=1.5,lty=2)
abline(v=cutoff,lwd=1)
abline(v=cutoff2,lwd=1)

lines(antibody1,fit.ab2$posterior[,1],lwd=2,col='blue')
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='purple')
legend(1125,0.8,c(expression(S^'-'),expression(S^'+')),lty=c(1,1),lwd=2,col=c('blue','purple'))}

#Plot histogram with cutoffs shown and normal distributions shown
{hist(antibody1, prob = TRUE, breaks=50, main = paste(antigen, "FMM"), 
  xlab="Normalized Log2(MFI Ratio)", cex.main=0.9, cex.lab=0.8, 
  cex.axis = 0.8, xlim=c(-2,8), ylim = c(0,0.5))
curve(dnorm(x, fit.ab2$mu[1], fit.ab2$sigma[1]), add=TRUE, col="darkblue", lwd=2)
curve(dnorm(x, fit.ab2$mu[2], fit.ab2$sigma[2]), add=TRUE, col="darkblue", lwd=2)
abline(v = multcutoffs[i,4:5], col = "red", lty = 2, lwd = 0.7, xpd=FALSE)}

remove(antigen, antibody1, cutoff, cutoff2, neg, pos, indet, fit.ab2)
```

29 - Pneumococcal.19A
```{r}
i = 29
#Select antigen
antigen <- multantnames[i]
antigen

#subset data for this antigen
singleant <- c(as.matrix(multants[i, (ncol(targetupdate)+1):ncol(multants)]))
#singleant <- singleant[singleant >= 0]

#put the data in numerical order - required to generate probability classification plot below
antibody1 <- sort(singleant)

#### Try FMM model first

fit.ab2<-normalmixEM(antibody1, lambda =c(0.5, 0.5), mu = c(2.332470, 4.162575),
sigma = c(1.007309, 0.858274), k = 2, fast=FALSE,maxit=10000,epsilon = 1e-16,maxrestarts=1000)

#5 Plot Cut off Value
summary(fit.ab2)

#cutoff below which is negative - manually set interval end points
cutoff<-uniroot(f,c(0,3),prob=0.90,lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=1)$root

#cutoff above which is positive - manually set interval end points
cutoff2<-uniroot(f2,c(3,6),prob=0.90, lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=2)$root

multcutoffs[i,4] <- cutoff
multcutoffs[i,5] <- cutoff2

#percentage positive 
pos <- sum(antibody1>cutoff2)/length(antibody1) * 100

#percentage negative
neg <- sum(antibody1<cutoff)/length(antibody1) * 100

#percentage indeterminate
indet <- (1-sum(antibody1>cutoff2)/length(antibody1)-sum(antibody1<cutoff)/length(antibody1)) *100

multprevalence[i,5] <- neg
multprevalence[i,6] <- pos
multprevalence[i,7] <- indet

#Plot cutoffs if there are two
{plot(antibody1,fit.ab2$posterior[,1],type='n',xlim=c(-4,10),lwd=2,ylim=c(0,1),col='green',las=1,xlab='Log2(MFI Ratio)',ylab='classification probability', main = paste(antigen, "FMM"))

rect(cutoff,-0.04,cutoff2,1.04,col='light grey',lwd=1.5)
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='red')

abline(h=0.90,lwd=1.5,lty=2)
abline(v=cutoff,lwd=1)
abline(v=cutoff2,lwd=1)

lines(antibody1,fit.ab2$posterior[,1],lwd=2,col='blue')
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='purple')
legend(1125,0.8,c(expression(S^'-'),expression(S^'+')),lty=c(1,1),lwd=2,col=c('blue','purple'))}

#Plot histogram with cutoffs shown and normal distributions shown
{hist(antibody1, prob = TRUE, breaks=50, main = paste(antigen, "FMM"), 
  xlab="Normalized Log2(MFI Ratio)", cex.main=0.9, cex.lab=0.8, 
  cex.axis = 0.8, xlim=c(-2,8), ylim = c(0,0.5))
curve(dnorm(x, fit.ab2$mu[1], fit.ab2$sigma[1]), add=TRUE, col="darkblue", lwd=2)
curve(dnorm(x, fit.ab2$mu[2], fit.ab2$sigma[2]), add=TRUE, col="darkblue", lwd=2)
abline(v = multcutoffs[i,4:5], col = "red", lty = 2, lwd = 0.7, xpd=FALSE)}

remove(antigen, antibody1, cutoff, cutoff2, neg, pos, indet, fit.ab2)
```

30 - Pneumococcal.33F
```{r}
i = 30
#Select antigen
antigen <- multantnames[i]
antigen

#subset data for this antigen
singleant <- c(as.matrix(multants[i, (ncol(targetupdate)+1):ncol(multants)]))
#singleant <- singleant[singleant >= 0]

#put the data in numerical order - required to generate probability classification plot below
antibody1 <- sort(singleant)

#### Try FMM model first

fit.ab2<-normalmixEM(antibody1, lambda =c(0.5, 0.5), k = 2, fast=FALSE,maxit=10000,epsilon = 1e-16,maxrestarts=1000)

#5 Plot Cut off Value
summary(fit.ab2)

#cutoff below which is negative - manually set interval end points
cutoff<-uniroot(f,c(0,3),prob=0.90,lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=1)$root

#cutoff above which is positive - manually set interval end points
cutoff2<-uniroot(f2,c(3,6),prob=0.90, lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=2)$root

multcutoffs[i,4] <- cutoff
multcutoffs[i,5] <- cutoff2

#percentage positive 
pos <- sum(antibody1>cutoff2)/length(antibody1) * 100

#percentage negative
neg <- sum(antibody1<cutoff)/length(antibody1) * 100

#percentage indeterminate
indet <- (1-sum(antibody1>cutoff2)/length(antibody1)-sum(antibody1<cutoff)/length(antibody1)) *100

multprevalence[i,5] <- neg
multprevalence[i,6] <- pos
multprevalence[i,7] <- indet

#Plot cutoffs if there are two
{plot(antibody1,fit.ab2$posterior[,1],type='n',xlim=c(-4,10),lwd=2,ylim=c(0,1),col='green',las=1,xlab='Log2(MFI Ratio)',ylab='classification probability', main = paste(antigen, "FMM"))

rect(cutoff,-0.04,cutoff2,1.04,col='light grey',lwd=1.5)
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='red')

abline(h=0.90,lwd=1.5,lty=2)
abline(v=cutoff,lwd=1)
abline(v=cutoff2,lwd=1)

lines(antibody1,fit.ab2$posterior[,1],lwd=2,col='blue')
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='purple')
legend(1125,0.8,c(expression(S^'-'),expression(S^'+')),lty=c(1,1),lwd=2,col=c('blue','purple'))}

#Plot histogram with cutoffs shown and normal distributions shown
{hist(antibody1, prob = TRUE, breaks=50, main = paste(antigen, "FMM"), 
  xlab="Normalized Log2(MFI Ratio)", cex.main=0.9, cex.lab=0.8, 
  cex.axis = 0.8, xlim=c(-2,8), ylim = c(0,0.5))
curve(dnorm(x, fit.ab2$mu[1], fit.ab2$sigma[1]), add=TRUE, col="darkblue", lwd=2)
curve(dnorm(x, fit.ab2$mu[2], fit.ab2$sigma[2]), add=TRUE, col="darkblue", lwd=2)
abline(v = multcutoffs[i,4:5], col = "red", lty = 2, lwd = 0.7, xpd=FALSE)}

remove(antigen, antibody1, cutoff, cutoff2, neg, pos, indet, fit.ab2)
```


31 - Poliovirus - negative population never reaches probability 0.9. Also, I tried to input values of mu ~ 1 and 2.2, with a range of sigma and lambda, but that forced the solution to the one I had previously selected of the 3 the FMM was giving without initial values specified.
```{r}
i = 31
#Select antigen
antigen <- multantnames[i]
antigen

#subset data for this antigen
singleant <- c(as.matrix(multants[i, (ncol(targetupdate)+1):ncol(multants)]))
#singleant <- singleant[singleant >= 0]

#put the data in numerical order - required to generate probability classification plot below
antibody1 <- sort(singleant)

#### Try FMM model first

fit.ab2<-normalmixEM(antibody1, lambda = c(0.0662692, 0.933731), 
mu = c(0.8811338, 1.812612), sigma= c(0.3076632, 0.666435), k = 2, fast=FALSE,maxit=10000,epsilon = 1e-16,maxrestarts=1000)

#5 Plot Cut off Value
summary(fit.ab2)

#cutoff below which is negative - manually set interval end points
#cutoff<-uniroot(f,c(0,3),prob=0.90,lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=1)$root

#cutoff above which is positive - manually set interval end points
cutoff2<-uniroot(f2,c(1,3),prob=0.90, lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=2)$root

#multcutoffs[i,4] <- cutoff
multcutoffs[i,5] <- cutoff2

#percentage positive 
pos <- sum(antibody1>cutoff2)/length(antibody1) * 100

#percentage negative
#neg <- sum(antibody1<cutoff)/length(antibody1) * 100

#percentage indeterminate
#indet <- (1-sum(antibody1>cutoff2)/length(antibody1)-sum(antibody1<cutoff)/length(antibody1)) *100

#multprevalence[i,5] <- neg
multprevalence[i,6] <- pos
#multprevalence[i,7] <- indet

#Plot cutoffs if there are two
{plot(antibody1,fit.ab2$posterior[,1],type='n',xlim=c(-4,10),lwd=2,ylim=c(0,1),col='green',las=1,xlab='Log2(MFI Ratio)',ylab='classification probability', main = paste(antigen, "FMM"))

#rect(cutoff,-0.04,cutoff2,1.04,col='light grey',lwd=1.5)
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='red')

abline(h=0.90,lwd=1.5,lty=2)
#abline(v=cutoff,lwd=1)
abline(v=cutoff2,lwd=1)

lines(antibody1,fit.ab2$posterior[,1],lwd=2,col='blue')
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='purple')
legend(1125,0.8,c(expression(S^'-'),expression(S^'+')),lty=c(1,1),lwd=2,col=c('blue','purple'))}

#Plot histogram with cutoffs shown and normal distributions shown
{hist(antibody1, prob = TRUE, breaks=50, main = paste(antigen, "FMM"), 
  xlab="Normalized Log2(MFI Ratio)", cex.main=0.9, cex.lab=0.8, 
  cex.axis = 0.8, xlim=c(-2,8), ylim = c(0,1.2))
curve(dnorm(x, fit.ab2$mu[1], fit.ab2$sigma[1]), add=TRUE, col="darkblue", lwd=2)
curve(dnorm(x, fit.ab2$mu[2], fit.ab2$sigma[2]), add=TRUE, col="darkblue", lwd=2)
abline(v = multcutoffs[i,5], col = "red", lty = 2, lwd = 0.7, xpd=FALSE)}

remove(antigen, antibody1, cutoff, cutoff2, neg, pos, indet, fit.ab2)
```

32 - Rh2_2030 - negative population never reaches probability 0.9. It gets really close though, the maximum posterior probability is 0.8963356. :(
```{r}
i = 32
#Select antigen
antigen <- multantnames[i]
antigen

#subset data for this antigen
singleant <- c(as.matrix(multants[i, (ncol(targetupdate)+1):ncol(multants)]))
#singleant <- singleant[singleant >= 0]

#put the data in numerical order - required to generate probability classification plot below
antibody1 <- sort(singleant)

#### Try FMM model first

fit.ab2<-normalmixEM(antibody1, lambda =c(0.5, 0.5), k = 2, fast=FALSE,maxit=10000,epsilon = 1e-16,maxrestarts=1000)

#5 Plot Cut off Value
summary(fit.ab2)

#cutoff below which is negative - manually set interval end points
#cutoff<-uniroot(f,c(-5,0),prob=0.90,lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=1)$root

#cutoff above which is positive - manually set interval end points
cutoff2<-uniroot(f2,c(-1,6),prob=0.90, lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=2)$root

#multcutoffs[i,4] <- cutoff
multcutoffs[i,5] <- cutoff2

#percentage positive 
pos <- sum(antibody1>cutoff2)/length(antibody1) * 100

#percentage negative
#neg <- sum(antibody1<cutoff)/length(antibody1) * 100

#percentage indeterminate
#indet <- (1-sum(antibody1>cutoff2)/length(antibody1)-sum(antibody1<cutoff)/length(antibody1)) *100

#multprevalence[i,5] <- neg
multprevalence[i,6] <- pos
#multprevalence[i,7] <- indet

#Plot cutoffs if there are two
{plot(antibody1,fit.ab2$posterior[,1],type='n',xlim=c(-4,10),lwd=2,ylim=c(0,1),col='green',las=1,xlab='Log2(MFI Ratio)',ylab='classification probability', main = paste(antigen, "FMM"))

#rect(cutoff,-0.04,cutoff2,1.04,col='light grey',lwd=1.5)
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='red')

abline(h=0.90,lwd=1.5,lty=2)
#abline(v=cutoff,lwd=1)
abline(v=cutoff2,lwd=1)

lines(antibody1,fit.ab2$posterior[,1],lwd=2,col='blue')
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='purple')
legend(1125,0.8,c(expression(S^'-'),expression(S^'+')),lty=c(1,1),lwd=2,col=c('blue','purple'))}

#Plot histogram with cutoffs shown and normal distributions shown
{hist(antibody1, prob = TRUE, breaks=50, main = paste(antigen, "FMM"), 
  xlab="Normalized Log2(MFI Ratio)", cex.main=0.9, cex.lab=0.8, 
  cex.axis = 0.8, xlim=c(-4,10), ylim = c(0,0.8))
curve(dnorm(x, fit.ab2$mu[1], fit.ab2$sigma[1]), add=TRUE, col="darkblue", lwd=2)
curve(dnorm(x, fit.ab2$mu[2], fit.ab2$sigma[2]), add=TRUE, col="darkblue", lwd=2)
abline(v = multcutoffs[i,5], col = "red", lty = 2, lwd = 0.7, xpd=FALSE)}

remove(antigen, antibody1, cutoff, cutoff2, neg, pos, indet, fit.ab2)
```

33 - Tg
```{r}
i = 33
#Select antigen
antigen <- multantnames[i]
antigen

#subset data for this antigen
singleant <- c(as.matrix(multants[i, (ncol(targetupdate)+1):ncol(multants)]))
#singleant <- singleant[singleant >= 0]

#put the data in numerical order - required to generate probability classification plot below
antibody1 <- sort(singleant)

#### Try FMM model first

fit.ab2<-normalmixEM(antibody1, lambda =c(0.5, 0.5), k = 2, fast=FALSE,maxit=10000,epsilon = 1e-16,maxrestarts=1000)

#5 Plot Cut off Value
summary(fit.ab2)

#cutoff below which is negative - manually set interval end points
cutoff<-uniroot(f,c(0,1),prob=0.90,lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=1)$root

#cutoff above which is positive - manually set interval end points
cutoff2<-uniroot(f2,c(1,6),prob=0.90, lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=2)$root

multcutoffs[i,4] <- cutoff
multcutoffs[i,5] <- cutoff2

#percentage positive 
pos <- sum(antibody1>cutoff2)/length(antibody1) * 100

#percentage negative
neg <- sum(antibody1<cutoff)/length(antibody1) * 100

#percentage indeterminate
indet <- (1-sum(antibody1>cutoff2)/length(antibody1)-sum(antibody1<cutoff)/length(antibody1)) *100

multprevalence[i,5] <- neg
multprevalence[i,6] <- pos
multprevalence[i,7] <- indet

#Plot cutoffs if there are two
{plot(antibody1,fit.ab2$posterior[,1],type='n',xlim=c(-4,10),lwd=2,ylim=c(0,1),col='green',las=1,xlab='Log2(MFI Ratio)',ylab='classification probability', main = paste(antigen, "FMM"))

rect(cutoff,-0.04,cutoff2,1.04,col='light grey',lwd=1.5)
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='red')

abline(h=0.90,lwd=1.5,lty=2)
abline(v=cutoff,lwd=1)
abline(v=cutoff2,lwd=1)

lines(antibody1,fit.ab2$posterior[,1],lwd=2,col='blue')
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='purple')
legend(1125,0.8,c(expression(S^'-'),expression(S^'+')),lty=c(1,1),lwd=2,col=c('blue','purple'))}

#Plot histogram with cutoffs shown and normal distributions shown
{hist(antibody1, prob = TRUE, breaks=50, main = paste(antigen, "FMM"), 
  xlab="Normalized Log2(MFI Ratio)", cex.main=0.9, cex.lab=0.8, 
  cex.axis = 0.8, xlim=c(-2,10), ylim = c(0,0.8))
curve(dnorm(x, fit.ab2$mu[1], fit.ab2$sigma[1]), add=TRUE, col="darkblue", lwd=2)
curve(dnorm(x, fit.ab2$mu[2], fit.ab2$sigma[2]), add=TRUE, col="darkblue", lwd=2)
abline(v = multcutoffs[i,4:5], col = "red", lty = 2, lwd = 0.7, xpd=FALSE)}

remove(antigen, antibody1, cutoff, cutoff2, neg, pos, indet, fit.ab2)
```

34 - Tg.GradeIII
```{r}
i = 34
#Select antigen
antigen <- multantnames[i]
antigen

#subset data for this antigen
singleant <- c(as.matrix(multants[i, (ncol(targetupdate)+1):ncol(multants)]))
#singleant <- singleant[singleant >= 0]

#put the data in numerical order - required to generate probability classification plot below
antibody1 <- sort(singleant)

#### Try FMM model first

fit.ab2<-normalmixEM(antibody1, lambda =c(0.5, 0.5), k = 2, fast=FALSE,maxit=10000,epsilon = 1e-16,maxrestarts=1000)

#5 Plot Cut off Value
summary(fit.ab2)

#cutoff below which is negative - manually set interval end points
cutoff<-uniroot(f,c(0,1),prob=0.90,lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=1)$root

#cutoff above which is positive - manually set interval end points
cutoff2<-uniroot(f2,c(1,6),prob=0.90, lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=2)$root

multcutoffs[i,4] <- cutoff
multcutoffs[i,5] <- cutoff2

#percentage positive 
pos <- sum(antibody1>cutoff2)/length(antibody1) * 100

#percentage negative
neg <- sum(antibody1<cutoff)/length(antibody1) * 100

#percentage indeterminate
indet <- (1-sum(antibody1>cutoff2)/length(antibody1)-sum(antibody1<cutoff)/length(antibody1)) *100

multprevalence[i,5] <- neg
multprevalence[i,6] <- pos
multprevalence[i,7] <- indet

#Plot cutoffs if there are two
{plot(antibody1,fit.ab2$posterior[,1],type='n',xlim=c(-4,10),lwd=2,ylim=c(0,1),col='green',las=1,xlab='Log2(MFI Ratio)',ylab='classification probability', main = paste(antigen, "FMM"))

rect(cutoff,-0.04,cutoff2,1.04,col='light grey',lwd=1.5)
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='red')

abline(h=0.90,lwd=1.5,lty=2)
abline(v=cutoff,lwd=1)
abline(v=cutoff2,lwd=1)

lines(antibody1,fit.ab2$posterior[,1],lwd=2,col='blue')
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='purple')
legend(1125,0.8,c(expression(S^'-'),expression(S^'+')),lty=c(1,1),lwd=2,col=c('blue','purple'))}

#Plot histogram with cutoffs shown and normal distributions shown
{hist(antibody1, prob = TRUE, breaks=50, main = paste(antigen, "FMM"), 
  xlab="Normalized Log2(MFI Ratio)", cex.main=0.9, cex.lab=0.8, 
  cex.axis = 0.8, xlim=c(-2,10), ylim = c(0,1))
curve(dnorm(x, fit.ab2$mu[1], fit.ab2$sigma[1]), add=TRUE, col="darkblue", lwd=2)
curve(dnorm(x, fit.ab2$mu[2], fit.ab2$sigma[2]), add=TRUE, col="darkblue", lwd=2)
abline(v = multcutoffs[i,4:5], col = "red", lty = 2, lwd = 0.7, xpd=FALSE)}

remove(antigen, antibody1, cutoff, cutoff2, neg, pos, indet, fit.ab2)
```

35 - TT
```{r}
i = 35
#Select antigen
antigen <- multantnames[i]
antigen

#subset data for this antigen
singleant <- c(as.matrix(multants[i, (ncol(targetupdate)+1):ncol(multants)]))
#singleant <- singleant[singleant >= 0]

#put the data in numerical order - required to generate probability classification plot below
antibody1 <- sort(singleant)

#### Try FMM model first

fit.ab2<-normalmixEM(antibody1, lambda =c(0.5, 0.5), k = 2, fast=FALSE,maxit=10000,epsilon = 1e-16,maxrestarts=1000)

#5 Plot Cut off Value
summary(fit.ab2)

#cutoff below which is negative - manually set interval end points
cutoff<-uniroot(f,c(0,3),prob=0.90,lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=1)$root

#cutoff above which is positive - manually set interval end points
cutoff2<-uniroot(f2,c(2,7),prob=0.90, lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=2)$root

multcutoffs[i,4] <- cutoff
multcutoffs[i,5] <- cutoff2

#percentage positive 
pos <- sum(antibody1>cutoff2)/length(antibody1) * 100

#percentage negative
neg <- sum(antibody1<cutoff)/length(antibody1) * 100

#percentage indeterminate
indet <- (1-sum(antibody1>cutoff2)/length(antibody1)-sum(antibody1<cutoff)/length(antibody1)) *100

multprevalence[i,5] <- neg
multprevalence[i,6] <- pos
multprevalence[i,7] <- indet

#Plot cutoffs if there are two
{plot(antibody1,fit.ab2$posterior[,1],type='n',xlim=c(-4,10),lwd=2,ylim=c(0,1),col='green',las=1,xlab='Log2(MFI Ratio)',ylab='classification probability', main = paste(antigen, "FMM"))

rect(cutoff,-0.04,cutoff2,1.04,col='light grey',lwd=1.5)
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='red')

abline(h=0.90,lwd=1.5,lty=2)
abline(v=cutoff,lwd=1)
abline(v=cutoff2,lwd=1)

lines(antibody1,fit.ab2$posterior[,1],lwd=2,col='blue')
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='purple')
legend(1125,0.8,c(expression(S^'-'),expression(S^'+')),lty=c(1,1),lwd=2,col=c('blue','purple'))}

#Plot histogram with cutoffs shown and normal distributions shown
{hist(antibody1, prob = TRUE, breaks=50, main = paste(antigen, "FMM"), 
  xlab="Normalized Log2(MFI Ratio)", cex.main=0.9, cex.lab=0.8, 
  cex.axis = 0.8, xlim=c(-2,10), ylim = c(0,0.5))
curve(dnorm(x, fit.ab2$mu[1], fit.ab2$sigma[1]), add=TRUE, col="darkblue", lwd=2)
curve(dnorm(x, fit.ab2$mu[2], fit.ab2$sigma[2]), add=TRUE, col="darkblue", lwd=2)
abline(v = multcutoffs[i,4:5], col = "red", lty = 2, lwd = 0.7, xpd=FALSE)}

remove(antigen, antibody1, cutoff, cutoff2, neg, pos, indet, fit.ab2)
```


36 - VZV.GradeIII - negative population never reaches probability of 0.9. Looks like could be a candidate for one population only (possible, depending on the background epi knowledge)
```{r}
i = 36
#Select antigen
antigen <- multantnames[i]
antigen

#subset data for this antigen
singleant <- c(as.matrix(multants[i, (ncol(targetupdate)+1):ncol(multants)]))
#singleant <- singleant[singleant >= 0]

#put the data in numerical order - required to generate probability classification plot below
antibody1 <- sort(singleant)

#### Try FMM model first

fit.ab2<-normalmixEM(antibody1, lambda =c(0.5, 0.5), k = 2, fast=FALSE,maxit=10000,epsilon = 1e-16,maxrestarts=1000)

#5 Plot Cut off Value
summary(fit.ab2)

#cutoff below which is negative - manually set interval end points
#cutoff<-uniroot(f,c(0,3),prob=0.90,lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=1)$root

#cutoff above which is positive - manually set interval end points
cutoff2<-uniroot(f2,c(0,2),prob=0.90, lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=2)$root

#multcutoffs[i,4] <- cutoff
multcutoffs[i,5] <- cutoff2

#percentage positive 
pos <- sum(antibody1>cutoff2)/length(antibody1) * 100

#percentage negative
#neg <- sum(antibody1<cutoff)/length(antibody1) * 100

#percentage indeterminate
#indet <- (1-sum(antibody1>cutoff2)/length(antibody1)-sum(antibody1<cutoff)/length(antibody1)) *100

#multprevalence[i,5] <- neg
multprevalence[i,6] <- pos
#multprevalence[i,7] <- indet

#Plot cutoffs if there are two
{plot(antibody1,fit.ab2$posterior[,1],type='n',xlim=c(-4,10),lwd=2,ylim=c(0,1),col='green',las=1,xlab='Log2(MFI Ratio)',ylab='classification probability', main = paste(antigen, "FMM"))

#rect(cutoff,-0.04,cutoff2,1.04,col='light grey',lwd=1.5)
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='red')

abline(h=0.90,lwd=1.5,lty=2)
#abline(v=cutoff,lwd=1)
abline(v=cutoff2,lwd=1)

lines(antibody1,fit.ab2$posterior[,1],lwd=2,col='blue')
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='purple')
legend(1125,0.8,c(expression(S^'-'),expression(S^'+')),lty=c(1,1),lwd=2,col=c('blue','purple'))}

#Plot histogram with cutoffs shown and normal distributions shown
{hist(antibody1, prob = TRUE, breaks=50, main = paste(antigen, "FMM"), 
  xlab="Normalized Log2(MFI Ratio)", cex.main=0.9, cex.lab=0.8, 
  cex.axis = 0.8, xlim=c(-2,8), ylim = c(0,1.5))
curve(dnorm(x, fit.ab2$mu[1], fit.ab2$sigma[1]), add=TRUE, col="darkblue", lwd=2)
curve(dnorm(x, fit.ab2$mu[2], fit.ab2$sigma[2]), add=TRUE, col="darkblue", lwd=2)
abline(v = multcutoffs[i,5], col = "red", lty = 2, lwd = 0.7, xpd=FALSE)}

remove(antigen, antibody1, cutoff, cutoff2, neg, pos, indet, fit.ab2)
```


6.For each antigen, select which model is better, FMM or K-means, and list that in the   "BestModel" column for that antigen in the cutoff data frame. 
7. Save the cutoff data frame as an r object and export as a .csv file. 

```{r}
#Display all of the cutoffs
multcutoffs

#Display all the prevalences 
multprevalence

#save the cutoffs in an R object to be imported later 
save(multcutoffs, file=paste0(study,"_twocutoffs"))
```


Currently unused script for K-means clustering:

### Try K Means Clustering 

#prepare matrix to store info about k means clusters
kcutoffs <- matrix(nrow = length(multantnames), ncol = 8)
 rownames(kcutoffs) <- multantnames                  
 colnames(kcutoffs) <- c("mean_low", "mean_high", "count_low", "count_high", "min_low", "min_high", "max_low", "max_high")

#run k means clustering
kclust <- kmeans(antibody1, centers = 2, nstart=20)
kclust

#prepare the clustering data
clustdata <- as.data.frame(cbind(antibody1, kclust$cluster))
colnames(clustdata) <- c("Ab_Response", "Cluster")
clustdata$Cluster <- factor(clustdata$Cluster, levels = c("1", "2"))
  
min_comp <- which(kclust$centers == min(kclust$centers))
max_comp <- which(kclust$centers == max(kclust$centers))

#calculate lambda (final mixing proportions), and sigma (sd) for each cluster
mix <- kclust$size/sum(kclust$size)
sdclust <- c(sd(clustdata[clustdata$Cluster == "1",1]), sd(clustdata[clustdata$Cluster == "2",1]))

#probability classification function to determine cutoffs
#cutoff below which is negative - manually set interval end points
cutoff<-uniroot(f,c(-3,4),prob=0.90,lambda=mix,mu=kclust$centers,sigma=sdclust,k=2,k1=1)$root

#cutoff above which is positive - manually set interval end points
cutoff2<-uniroot(f2,c(4,9),prob=0.90,lambda=fit.ab2$lambda,mu=fit.ab2$mu,sigma=fit.ab2$sigma,k=2,k1=2)$root

multcutoffs[i,2] <- cutoff
multcutoffs[i,3] <- cutoff2

#percentage positive 
pos <- sum(antibody1>cutoff2)/length(antibody1) * 100

#percentage negative
neg <- sum(antibody1<cutoff)/length(antibody1) * 100

#percentage indeterminate
indet <- (1-sum(antibody1>cutoff2)/length(antibody1)-sum(antibody1<cutoff)/length(antibody1)) *100

multprevalence[i,2] <- neg
multprevalence[i,3] <- pos
multprevalence[i,4] <- indet

#calculate posterior probability for the k means clustering (this is done automatically in the FMM) - I have a great online tutorial for this, but from that I have learned that the k means clustering is like a step along the way in the mixture model, and therefore using k means and then the probability classification function is very similar to making my own mixture model without the iteration and convergence part of the process. Also, I think that due to the known different sources / latent variables, this whole process is not really right, not necessarily going to work. But perhaps what I should be doing is maximum likelihood estimation using the two latent classes (country) and then going from there. for now I am going to go forward trying the FMM with two or three populations and go from there. 

posterior <- function( ){
  
  
  
}


#Plot cutoffs
{plot(antibody1,fit.ab2$posterior[,1],type='n',xlim=c(-4,10),lwd=2,ylim=c(0,1),col='green',las=1,xlab='Log2(MFI Ratio)',ylab='classification probability', main = paste(antigen, "K-means Clustering"))

rect(cutoff,-0.04,cutoff2,1.04,col='light grey',lwd=1.5)
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='red')

abline(h=0.90,lwd=1.5,lty=2)
abline(v=cutoff,lwd=1)
abline(v=cutoff2,lwd=1)

lines(antibody1,fit.ab2$posterior[,1],lwd=2,col='blue')
lines(antibody1,fit.ab2$posterior[,2],lwd=2,col='purple')
legend(1125,0.8,c(expression(S^'-'),expression(S^'+')),lty=c(1,1),lwd=2,col=c('blue','purple'))}

#Plot histogram with cutoffs shown and normal distributions shown
{hist(antibody1, prob = TRUE, breaks=50, main = paste(antigen, "K-means Clustering"), xlab="Normalized Log2(MFI Ratio)", cex.main=0.9, cex.lab=0.8, 
  cex.axis = 0.8, xlim=c(-4,9), ylim = c(0,0.5))
curve(dnorm(x, fit.ab2$mu[1], fit.ab2$sigma[1]), add=TRUE, col="darkblue", lwd=2)
curve(dnorm(x, fit.ab2$mu[2], fit.ab2$sigma[2]), add=TRUE, col="darkblue", lwd=2)
abline(v = multcutoffs[i,2:3], col = "red", lty = 2, lwd = 0.7, xpd=FALSE)}

kcutoffs[i, "min_low"] <- min(clustdata$Ab_Response[which(clustdata$Cluster == min_comp)])
kcutoffs[i, "max_low"] <- max(clustdata$Ab_Response[which(clustdata$Cluster == min_comp)])
kcutoffs[i, "min_high"] <- min(clustdata$Ab_Response[which(clustdata$Cluster == max_comp)])
kcutoffs[i, "max_high"] <- max(clustdata$Ab_Response[which(clustdata$Cluster == max_comp)])

kcutoffs[i, "mean_low"] <- mean(clustdata$Ab_Response[which(clustdata$Cluster == min_comp)])
kcutoffs[i, "mean_high"] <- mean(clustdata$Ab_Response[which(clustdata$Cluster == max_comp)])

kcutoffs[i, "count_low"] <- length(clustdata$Ab_Response[which(clustdata$Cluster == min_comp)])
kcutoffs[i, "count_high"] <- length(clustdata$Ab_Response[which(clustdata$Cluster == max_comp)])


